### 2022-01-06 manuscript/Draft_0.0.tex
DC initial commit

\documentclass[aps,onecolumn,preprintnumbers,amsmath,amssymb,nofootinbib,superscriptaddress,notitlepage]{revtex4-1}

\usepackage{epsfig}
\usepackage[utf8]{inputenc}
\usepackage[dvipsnames]{xcolor}
\usepackage[normalem]{ulem}
%\usepackage{slashed}
\usepackage{caption}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{bbold}
\usepackage{amssymb,latexsym}
\usepackage{amsmath,amsbsy,bbm}

\newcommand{\reales}{{\rm R}\hspace{-1ex}\rule{0.1mm}{1.5ex}\hspace{1ex}}
\def\tstrut{\vrule height2.5ex depth0pt width0pt} % used in tables
\def\jtstrut{\vrule height5ex depth0pt width0pt} % used in tables

\newcommand{\eftnopi}{\mbox{EFT$(\not \! \pi)$}}

\definecolor{green}{HTML}{2E8B57}
\interfootnotelinepenalty=10000 %% Completely prevent breaking of footnote

\begin{document}

%\title{Universally emergent L=1 resonances}
\title{Four-body L=1 systems from contact EFT}

\author{Johannes Kirscher}
\address{Theoretical Physics Division, School of Physics and Astronomy,\\
  The University of Manchester, Manchester, M13 9PL, UK}

\author{Martin Sch{\"a}fer}
\address{Nuclear Physics Institute of the Czech Academy of Sciences, 25069 \v{R}e\v{z}, Czech Republic}

\author{Rimantas Lazauskas}
\address{IPHC, IN2P3-CNRS/Universit\'e de Strasbourg BP 28, F-67037 Strasbourg Cedex 2, France}

\author{Lorenzo Contessi}\email{lorenzo@contessi.net}
\address{IRFU, CEA, Universit\'e Paris-Saclay, 91191 Gif-sur-Yvette, France}

\author{Jaume Carbonel}
\address{Universit\'e Paris-Saclay, CNRS/IN2P3, IJCLab, 91405 Orsay, France}

\date{\today}

\begin{abstract} 
Few-body scattering resonances appear in multiple physical fields and are commonly found in experiments. 
Compared with boundstates, they are more difficult to be studied theoretically and numerically because of their belonging to the continuum phase-space.
In this study we analyze the minimal theory that predict the appearance of $L=1$ four-body resonance.
This state is known in nuclear physics to be related with the lighter nucleus that show resonant behaviour: $^4$H.
However, we aim not only to study it in the nuclear framework, but also in more general universal systems.
For this purpose we employ a contact effective field theory both fitted on nuclear observables (pionless effective field theory) and to unitary systems (universal effective field theory).
This study will help to understand how resonances emerges in few- and many-body systems for nuclear physics and any other physical field close to universality.
\end{abstract}

\maketitle

\section{Introduction}

Resonance are ever present in quantum and classical physics.
However, especially in many-particle quantum fields as hadronic, nuclear, and atomic physics, they are far from been trivial to be predicted and calculated. 
A resonance in these fields is generally consequence of a nonperturbative and complex interplay of particle interactions that leads to the existence of multiple excitation and thresholds. 
They are also, generally difficulty to be experimentally measured because of their broad size and their many-body nature. 
Many models predict the existence of resonant states with better or worse success, however, just looking at the Hamiltonian of a system it is hard to foreseen the existence of such states.
In this study we approach the existence of a resonant pole in the $^4$H nucleus using a minimal interaction: a renormalizable contact effective field theory at leading order.
$^4$H is known to be the smallest nucleus that was measured to have a (relatively broad) resonance and it is the getaway to study the mechanism that creates resonances in nuclear systems and nuclear theories.

In the last years effective field theories (EFT) have had a ever-increasing impact on nuclear and atomic physics. 
They relay on the expansion of the appropriate underline theory onto a set of operators hierarchically arranged in a powercounting. 
The origin of this expansion depends on the kind system in study and the interparicle typical momentum exchanged, and differentiate an EFT from another. 
For example, it was shown that few-body nuclear systems are close to the unitary limit, in which the two-body scattering length is much larger than any other scale in such systems, allowing the description of few nucleons expanding the EFT around an infinite (or large) scattering length.
This takes the name of pionless powercounting (\eftnopi) and, on contrary to the chiral EFT, in which pions origin long range forces, it is an expansion in contact operators.
The absence of pions in \eftnopi limits this theory to be a low-momentum theory (i.e. can not describe phenomena which typical momentum would allow the creation of pions) but allows it to be fully renormalizable and relatively easy to be treated numerically and analytically.
This makes it best suited to understand in simple terms even complex many-body phenomena and for the description of very shallow quantum states, like resonant poles.

To access the presence of a resonant state in $^4$H with a contact EFT we first, fix a \eftnopi on nuclear observables (fixing the nuclon mass, and the deuterium and triton bindings).
The same theory was also fixed to nucler systems in which the two-body potential was tuned to the unitarity limit.
This last case allows the access to the universal limit and to the deviation of the nuclear potential from it.
We chose to use a SU(4) symmetric theory in both case for simplicity as this was proven to be a good first order representation of nuclear physics\cite{}.

In both the cases the theory has a contact nature, that results in the Thomas collapse, i.e. a diverging three-body energy as the theory approach the contact limit.
To avoid this, and to fix the theory to a physical and finite three-body energy, a contact three-body repulsive interaction is promoted at the theory LO.
In the physical case this vertex is fitted to reproduce the $^3$He energy and in the unitary case to fix a three-body binding $B_3=0.01$.
In the unitary case the three-body counterterm represent the inclusion of a new scale in the problem (and the only one present), therefore, this inclusion breaks the scale invariance typical of universal theories into a discrete version of it with the consequent appearance of a tower of Efimov states in the three-body system.

\section{Contact EFT and numerical methods}

\begin{table}[]
    \centering
    \begin{tabular}{|ccc|}
    \hline
    \multicolumn{3}{|c|}{Nuclear LECs}\\
    \hline
         $\Lambda$ [fm$^{-1}$] & $C_0$ [MeV] & $D_0$ [MeV] \\
1   &	-44.4552	&	27.2312 \\
2	&   -142.376	&	172.703 \\
3	&   -295.959	&	559.013 \\
4	&   -505.202	&	1397.56 \\
6	&   -1090.66	&	6311.30 \\
10	&   -2929.48	&	89436.2 \\
    \hline
    \end{tabular}
    \quad
\begin{tabular}{|ccc|}
    \hline
    \multicolumn{3}{|c|}{Universal LECs}\\
    \hline        
        $\Lambda$  & $C_0$  & $D_0$  \\
1	&   -0.671	&	0.678 \\
2	&   -2.684	&	7.749 \\
4	&   -10.736	&	194.253 \\
6	&   -24.156	&	4273.294 \\
8	&   -42.944	&	122391.358 \\
10	&   -67.100	&	4102409.239 \\
    \hline
\end{tabular}
    \caption{LECs fitted for each cut-off. In the left tab are listed the LECs fitted to reproduce deuterium and $^3$He energy in MeV. On the right the ones that reproduce unitary sistems of particles with $m=\hbar=c=1$.}
    \label{tab:my_label}
\end{table}

The leading order (LO) of the theory is composed by a contact two-body and a contact three-body operators with two low energy constants (LECs) to be fitted on physical observables. 
A Gaussian regulator and a cut-off $\Lambda$ are introduced to smear the contact potential such that the contact limit is achieved for $\Lambda\rightarrow+\infty$:

\begin{equation}
    V(\textbf{r})=C_0 \sum_{i,j}^N e^{-\frac{r_{ij}^2\Lambda^2}{4}}
\end{equation}

\begin{equation}
    W(\textbf{r})=D_0 \sum_{ijk}^N \left[
    e^{-\frac{(r_{ij}^2+r_{ik}^2)\Lambda^2}{4}}+
    e^{-\frac{(r_{ij}^2+r_{jk}^2)\Lambda^2}{4}}+
    e^{-\frac{(r_{jk}^2+r_{ik}^2)\Lambda^2}{4}}\right]
\end{equation}

Once the interaction is regularized the LECs ($C_0$ and $D_0$) become cut-off dependent and should be fitted for any $\Lambda$ to reproduce the chosen set of fixed two- and three-body observables.
Nonetheless, if the theory is renormalizable this is sufficient to stabilize any other few- and many-body observable in the \textbf{large cut-off limit} .
Two set of LECs are reported in tab. \ref{tab:my_label}, one for the nuclear and one for the unitary case.
The nuclear LECs are fitted to reproduce a single two-body boundstate of $B_2=2.22$ MeV (both in singlet and triplet channels).
The three body is fitted to reproduce a single three-body state $B_3=-8.482$ MeV with a nucleon mass is fixed to $m=938.858$ MeV with $\hbar c= 197.31613$.
The universality LECs are fitted to reproduce a large two body scattering length ($a_2>10^5$) and a single three body state $B_3=0.01$ with a particle mass fixed to be $m=1$ and $\hbar=c=1$.
The fitting procedure has been done solving the two-body Shr\"odinger equation with the Numerov method and the three-body using the stochastic variational method briefly described below.

\subsection{Numerical methods}
RGM - SVM - ACCC - ?

\section{Goals and results}

The final goal of the project is the calculation of $^4$H and the respective unitary fermion system (AABC) $L=1$ resonant poles.
However, a set of benchmark can be done in smaller systems to crosscheck the different numerical methods.
Examples of such observables are the dimer-dimer scattering length (a(nn-nn) in nuclear physics) expected to be 0.6 time the two body scattering length in the unitary case, four distinguishable particles bounstate ($^4$He energy) expected to be 4.6 $E_3$ in the unitary case, and the particle-trimer scattering length (a(n-$^3$He)) with zero angular momentum.
Given the variety of methods that we employ I suggest to start from the nuclear case (to have a experimental crosscheck) and then to move to the unitary case once we are relatively sure the numeric is under control. 
Notice that the $^4$He energy is expected to be understimated (may be around $B_4\sim 20$MeV) by the theory since we are using the SU(4) symmetry fixing the deuterium boundstate. 
a(n-$^3$He) is a good benchmark for RGM and Rimas's method but not very convenient for SVM. In that case it may be useful to set a four-body potential attractive enough to bind $^4$H for a finite cut-off (e.g. 2 fm$^{-1}$) and to check consistency of the methods.

\end{document}

### 2022-01-06 manuscript/Draft_0.1.tex
DC initial commit

\documentclass[aps,onecolumn,preprintnumbers,amsmath,amssymb,nofootinbib,superscriptaddress,notitlepage]{revtex4-1}

\usepackage{epsfig}
\usepackage[utf8]{inputenc}
\usepackage[dvipsnames]{xcolor}
\usepackage[normalem]{ulem}
%\usepackage{slashed}
\usepackage{caption}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{bbold}
\usepackage{amssymb,latexsym}
\usepackage{amsmath,amsbsy,bbm}

\newcommand{\reales}{{\rm R}\hspace{-1ex}\rule{0.1mm}{1.5ex}\hspace{1ex}}
\def\tstrut{\vrule height2.5ex depth0pt width0pt} % used in tables
\def\jtstrut{\vrule height5ex depth0pt width0pt} % used in tables

\newcommand{\eftnopi}{\mbox{EFT$(\not \! \pi)$}}

\definecolor{green}{HTML}{2E8B57}
\interfootnotelinepenalty=10000 %% Completely prevent breaking of footnote

\begin{document}

%\title{Universally emergent L=1 resonances}
\title{Four-body L=1 systems from contact EFT}

\author{Johannes Kirscher}
\address{Theoretical Physics Division, School of Physics and Astronomy,\\
  The University of Manchester, Manchester, M13 9PL, UK}

\author{Martin Sch{\"a}fer}
\address{Nuclear Physics Institute of the Czech Academy of Sciences, 25069 \v{R}e\v{z}, Czech Republic}

\author{Rimantas Lazauskas}
\address{IPHC, IN2P3-CNRS/Universit\'e de Strasbourg BP 28, F-67037 Strasbourg Cedex 2, France}

\author{Lorenzo Contessi}\email{lorenzo@contessi.net}
\address{IRFU, CEA, Universit\'e Paris-Saclay, 91191 Gif-sur-Yvette, France}

\author{Jaume Carbonel}
\address{Universit\'e Paris-Saclay, CNRS/IN2P3, IJCLab, 91405 Orsay, France}

\date{\today}

\begin{abstract} 
(to be cleaned at the end)
Few-body scattering resonances appear in multiple physical fields and are commonly found in experiments. 
Compared with boundstates, they are more difficult to be studied theoretically and numerically because of their belonging to the continuum phase-space.
In this study, we analyze the minimal theory that predicts the appearance of $L=1$ four-body resonance.
This state is known in nuclear physics to be related to the lighter nucleus that shows resonant behavior: $^4$H.
However, we aim not only to study it in the nuclear framework but also in more general universal systems.
For this purpose, we employ a contact effective field theory both fitted on nuclear observables (pionless effective field theory) and to unitary systems (universal effective field theory).
This study will help to understand how resonances emerge in few- and many-body systems for nuclear physics and any other physical field close to universality.
\end{abstract}

\maketitle

\section{Introduction}

Resonances are ever-present in quantum and classical physics.
However, especially in many-particle quantum fields as hadronic, nuclear, and atomic physics, they are far from been trivial to be predicted and calculated. 
A resonance in these fields is generally a consequence of a nonperturbative and complex interplay of particle-particle interactions and open channels that leads to the existence of multiple excitation and thresholds. 
The broad size and many-body nature make these states also relatively hard to be identified experimentally. 
Although many models predict the existence of resonant states with better or worse success, just looking at the Hamiltonian of a system it is hard to foresee their existence, and the numerical methods that can extract complex energy are, in general, expensive or less accurate than the ones developed for bound states.
%

%
Among nuclear systems with resonances, $^4$H $J^\pi=1^-$ has a special role and has been object of several studies as it is known to be the smallest nucleus with a (relatively broad) resonance.
%
In particular, cross-sections and scattering parameters have been studied extensively experimentally (e.g. \cite{osti_4230875, Phillips:1980zz, Tilley:1992zz}) and theoretically.
Concerning the theoretical side, several interactions and different numerical methods have been tested
(see, e.g. \cite{Ciesielski:1997vy,Ciesielski:1998sy,Ciesielski:1999pp,Viviani:1998gr,Fonseca:1999zz,Lazauskas:2004uq}) to predict well phaseshifts especially for low-energy scattering.
%
Fewer studies can be found, instead, about the position of the $^4$H resonance pole that induces such phaseshift. 
In \cite{Arai:2003ek,deDiego:2007rd,Lazauskas:2019cxj} the resonance position of $^4$H is extracted using respectively, RGM (which will be explained in the next sections of this paper), two-body $n-t$ potential, and three microscopic potentials with a Faddeev-Yakubovsky solver. 
The theoretical models agree for the presence of a $J^\pi=1^-$ resonance pole with energy $Re(E)=\{0.90 - 1.23\}$ MeV and width $\Gamma=\{3.5 - 5.8\}$ MeV.
Experimentally, the resonant pole can be extracted by R-matrix analysis to be at $Re(E)=3.50$ MeV and  $\Gamma=6.73$ MeV \cite{Tilley:1992zz}.
Although there is no precise agreement among experiment and models on the energy position of this resonant pole, the ability to create it in such models is still remarkable and has intrinsic value in the interpretation of the experimental cross-section.
%
The importance of studying $^4$H resonances and of the theoretical mechanisms that create it exceed the description of the system itself. 
It is the getaway for larger systems: on one hand for many-neutrons, on the direction of studying the stability of neutron tears and eventually to the neutron star equation of state.
On the other hand, to the study of resonances in heavy nuclei that are nowadays still hard or even impossible from ab-initio principles. 
%
In this study, we are interested in both these aspects on the framework of very minimalists nuclear forces: renormalizable contact effective field theories. 
%

%
In the last years, effective field theories (EFT) have had an ever-increasing impact on nuclear and atomic physics. 
They rely on the expansion of the appropriate underline theory onto a set of operators hierarchically arranged in a powercounting. 
The origin of this expansion depends on the kind of system in study and of the interparticle typical momentum exchanged, and differentiate an EFT from another. 
For example, it was shown that few-body nuclear systems are close to the unitary limit, in which the two-body scattering length is much larger than any other scale in such systems, allowing the description of few nucleons expanding the EFT around an infinite (or large) scattering length (see \cite{vanKolck:1999mw}).
This takes the name of pionless powercounting (\eftnopi) and, contrary to the chiral EFT, in which pions origin long-range forces, it is an expansion in contact operators.
The absence of pions in \eftnopi limits this theory to be a low-momentum theory (i.e. can not describe phenomena which typical momentum would allow the creation of pions) but allows it to be fully renormalizable and relatively easy to be treated numerically and analytically.
This makes it best suited to understand in simple terms even complex many-body phenomena and for the description of very shallow quantum states, like resonant poles. 
In the last years, \eftnopi was proven to be a valuable theory to study the behavior of many-boson systems and nuclei up to four nucleons. 
However, the LO of the theory does not appear to perform as well for the behavior of multi-fermionic systems, on which it erroneously predicts unbound nuclei above four particles (eg. $^7$Li and $^{16}$O) \cite{Schafer:2020ivj,Contessi:2017rww}.
The reason for this is to be attributed to the theory's more general inability of creating bound mixed symmetry states.
However, the subleading order of the EFT may still be able to correct this behavior provided that the LO creates, at least, an unbound state (virtual o resonant) that can be moved to the correct bound position. 
On the contrary, if no state is present at LO in these systems, of which $^4$H is the minimal representative, only a modification of the powercounting, and therefore of the entire theory, will allow for the correct description of nuclear physics using contact EFTs.
The creation of resonant poles in LO \eftnopi is possible, as it was shown in $nn\Lambda$ systems \cite{Schafer:2020rba} (as a subthreshold resonance), however, there is no record of such poles created in systems with mixed symmetry groundstates as $^4$H. 
By approaching the existence of a resonant pole in $^4$H we are tackling two problems at the same time: the possibility of creating resonances with the barest possible interaction and the fact that contact EFT can or not describe nuclear physics.
%

%
To access this state we first fix a \eftnopi on nuclear observables (fixing the nucleon mass, and the deuterium and triton bindings).
The same theory was also fixed to nuclear systems in which the two-body potential was tuned to the unitary limit.
This last case allows access to the universal limit and the deviation of the nuclear potential from it.
We chose to use a SU(4) symmetric theory in both cases for simplicity as this was proven to be a good first-order representation of nuclear physics \cite{Konig:2016utl}.

\section{Contact EFT and numerical methods}

\begin{table}
    \centering
    \begin{tabular}{|ccc|}
    \hline
    \multicolumn{3}{|c|}{Nuclear LECs}\\
    \hline
         $\Lambda$ [fm$^{-1}$] & $C_0$ [MeV] & $D_0$ [MeV] \\
1   &	-44.4552	&	27.2312 \\
2	&   -142.376	&	172.703 \\
3	&   -295.959	&	559.013 \\
4	&   -505.202	&	1397.56 \\
6	&   -1090.66	&	6311.30 \\
10	&   -2929.48	&	89436.2 \\
    \hline
    \end{tabular}
    \quad
\begin{tabular}{|ccc|}
    \hline
    \multicolumn{3}{|c|}{Universal LECs}\\
    \hline        
        $\Lambda$  & $C_0$  & $D_0$  \\
1	&   -0.671	&	0.678 \\
2	&   -2.684	&	7.749 \\
4	&   -10.736	&	194.253 \\
6	&   -24.156	&	4273.294 \\
8	&   -42.944	&	122391.358 \\
10	&   -67.100	&	4102409.239 \\
    \hline
\end{tabular}
    \caption{LECs fitted for each cut-off. In the left tab are listed the LECs fitted to reproduce deuterium and $^3$He energy in MeV. On the right the ones that reproduce unitary systems of nuclei.}
    \label{tab:LECs_unprojected}
\end{table}

The leading order (LO) of the contact EFT we are employing consists of a contact two-body and a contact three-body operators with two low energy constants (LECs) to be fitted on physical observables \cite{vanKolck:1999mw}. 
A Gaussian regulator and a cut-off $\Lambda$ are introduced to smear the potential such that the contact limit is restored for $\Lambda\rightarrow+\infty$:

\begin{equation}
    V(\textbf{r})=C_0 \sum_{i,j}^N e^{-\frac{r_{ij}^2\Lambda^2}{4}}
\end{equation}

\begin{equation}
    W(\textbf{r})=D_0 \sum_{ijk}^N \left[
    e^{-\frac{(r_{ij}^2+r_{ik}^2)\Lambda^2}{4}}+
    e^{-\frac{(r_{ij}^2+r_{jk}^2)\Lambda^2}{4}}+
    e^{-\frac{(r_{jk}^2+r_{ik}^2)\Lambda^2}{4}}\right].
\end{equation}

Once the interaction is regularized the LECs ($C_0$ and $D_0$) become cut-off dependent and must be fitted for any $\Lambda$ to reproduce the chosen set of fixed two- and three-body observables.
Nonetheless, if the theory is renormalizable this is sufficient to stabilize (in the sense of converging to a finite value) any other few- and many-body observable in the \textit{large cut-off limit}.
We employ two different two-body potentials in this study, a central one and one projected in S-wave only. 
This division is necessary for the numerical methods we use but is relevant only for small cut-offs.
In fact, in the limit, $\Lambda\rightarrow\infty$, the projected and unprojected potentials converge to the same contact interaction essentially representing only a different choice of the regulator.
Nonetheless, for small cut-off we expect and experience discrepancies, this results especially in different sets of three-body LEC $D_0$ that fix the three-body energy.
Moreover, for each projected and unprojected interaction we fit two sets of LECs.
The first, the "nuclear" one, fixes a single two-body boundstate of $B_2=2.22$ MeV (both in singlet and triplet channels).
In the second, the "universal" ones, the LECs are fitted to reproduce a large two-body scattering length ($a_0>10^5$).
In both cases, the three-body is fitted to reproduce a single three-body boundstate $B_3=-8.482$ MeV, and we employ the same nucleon mass to $m=938.858$ MeV, and the same $\hbar c= 197.31613$.
As an example, in tab. \ref{tab:LECs_unprojected}, we report the nuclear and universal LECs for the unprojected interaction.
%

%
Since \eftnopi is best suited for the description of low energy observables we refer to the effective range expansion (ERE) scattering parameter. 
It is essentially the expansion in low momentum of the phaseshift of a relative angular momentum $L$ two-body problem phaseshift $\delta$:

\begin{equation}
    k^{2L+1}cot(\delta)=-\frac{1}{a_L}+\frac{1}{2}r_L k^2 + ... \, .
\end{equation}

The same expansion can be used either in the two-body problem and in the four-body one assuming that $^4$H can be seen as a $n-^3$H pair.
Resonances will therefore emerge as poles of the system T-matrix

\begin{equation}
T = \frac{1}{k^{2L+1}cot(\delta)-ik}    
\end{equation}

and can be extracted either by fitting phaseshifts to the ERE formula or directly through solving the Schr\"odinger equation for complex energies.

\subsection*{Numerical methods}

In this work, we utilize three different methods to solve the $n-^3$H shr\"oedinger equation.
The Rimas Method, the Stochastic Variational Method, and the Resonating Group Method. 
Coupled with these technologies we use also the complex rotation and the Analytic Continuation of the Coupling Constant (ACCC) to determine the position of resonant solution of the four-body problem (belonging to the continuum and hard to be extracted with the conventional methods) and the scattering lengths and volumes of the $n-^3H$ reaction.

**wrong and to be changed** 
SVM consists of the variational search of the ground state of the problem using an over-complete set of Gaussians, chosen stochastically for each Jacobi coordinate, to represent the system wave function. 
This few-body method was developed by Lee Suzuki [] in ... and refined during the years to provide a reliable and relatively cheap solver for ground-state system up to $\sim 6$ particles.
A review of the method can be found in [] and a deeper insight is given by [].

%
%- Just give an idea and the references -
%
%
% RGM - SVM - ACCC - ?
%

%
%
%
%
%
%
%
%
%
%

\section{Procedure and results}

\begin{figure}
\centering
\includegraphics[width=0.95\textwidth]{./Graphs/a0a1} 
\caption{$1^-$ resonant pole in $^4$H}
\label{fig:a0a1}
\end{figure}

Our discussion begins with the analysis of low energy scattering parameters of the $n-^3$H system. 
This system allows for several low-energy states with relative angular momentum $J=1$ between the fragments: $0^-$, $1^-$, and $2^-$; we focus exclusively on the natural parity state: $1^-$. 
We also study the state $0^+$, with relative angular momentum L=$0$. 
This state is Pauli excluded, therefore, we do not expect any resonant or bound state in this channel but we still consider it interesting to study the EFT behavior and as a benchmark among different methods.
In figure \ref{fig:a0a1} we shown the scattering length and volume (relative to $0^+$ and $1^-$ states) calculated using SVM and RIMAS microscopical approaches.
Can be noticed how, for large enough cutoffs, the two methods are compatible.
This was expected since the two calculations use effectively two different regulators due to the presence of an S-wave projected and unprojected two-body potential. 
The difference between the two is more noticeable in the $J^\pi=1^-$ channel as the effect of P-wave interactions is more evident.
The two scattering parameters converge with the cut-off to a finite value. 
This fact is nontrivial since the interparticle interaction converges to a contact potential for large cut-offs.
In fact, $n$ and $^3H$ contain an identical fermion which suppresses any positive parity interaction.
However, the contact nature of the potential allows only particles in relative S-wave to interact. 
The finiteness of $a_0$ and $a_1$ should, therefore, be explained by the mediation of the distinguishable fermions and by the few-body effects.
$a_0$ and $a_1$ converge, empirically, as $1/\lambda$. 
In other words, since the interplay of S-wave interactions can result in a finite interaction in P-wave among few-body clusters, the scattering length/volume remains finite even only including the theory LO.
As a consequence, their cut-off behavior is $\propto1/\Lambda$ as expected by LO observables.
The sign and magnitude of the converged results ($a_0\simeq 3.1$ fm and $a_1\simeq-13(1)$) indicate the absence of boundstates, but the $a_1$ magnitude might indicate the presence of a shallow pole in the $1^-$ system.
It is also interesting to notice that the effective range for $0^+$ and $1^-$ remains also finite ($r_0\simeq2$ fm and $r_1\simeq1$ fm respectively).
This is also expected since, despite the nucleon-nucleon interaction is of contact nature, the size of the fragments remains finite, allowing for an inter-fragment long-range effect.
%

While arguably the best method to extract phaseshifts and resonance positions, the microscopic approach becomes more and more complicated and unfeasible when the number of particles is increased. 
For this, we would like to tackle the same problem from a different perspective: using the RGM formalism.
RGM intrinsically contains an approximation in the form of a simplified few-body wave function of one of the fragments.
It is, however, easily extendable to larger systems.
In our case, RGM transform a four-body problem into a simplified two-fragment one at the price of

%
%
\begin{figure}
\centering
\includegraphics[width=0.95\textwidth]{./Graphs/E4H} 
\caption{$1^-$ resonant pole in $^4$H}
\label{fig:Resonance_pole}
\end{figure}
%

%
The second step in our calculation is the determination of the $J^\pi=1^-$ nuclear resonance position in the Energy complex plane. 
This has been done using the ACCC method starting from "RIMAS" numerical method. 
In figure \ref{fig:Resonance_pole}, the evolution of such pole can be follow to pass the threshold energy $B_{t}=8.484$ MeV ($Re(E)=0$ in the plot) to stabilize around $E_{n-t}=-8.7-i\,3.1$ for cutoffs greater than $6$ fm$^{-1}$.
This represents a shallow and broad subthreshold resonance. 
The presence of such a state and especially its stability (in this case expressed as a pole that does not run to infinite energy increasing the cut-off) is not trivial for the same reasons as one might not expect scattering length/volumes larger than zero.
%
Therefore, this proves that the theory is able to predict shallow states in systems with mixed symmetry. 
However, the position of the LO EFT pole appears to not be compatible with the physical resonance in $^4H$: ??? ($E_{n-t}=8.17+i\,6.73$). %\cite{http://tunlweb.tunl.duke.edu/nucldata/ourpubs/04_1992.pdf}. where does this come from? ???
Nonetheless, the theory is only tested at LO where the relevant operators to describe such states are not been yet introduced.
It is not in principle problematic that the LO pole is not consistent with the experimental data since including the subleading orders (NLO and N$^2$LO) can, even in a perturbative treatment of the expansion, relocate it in the correct position.
However, in this process one should be careful that the insertion of the subleading operators does not shift unreasonably, neither too much nor in the wrong direction, any of the other observables (e.g. the $^4He$ energy or the $n-^2H$ phaseshifts). 
At the current knowledge of the authors, no studies have ever been done in this sense and the possibility of a consistent correction of a resonant pole in therms of powerconting hierarchy remains to be demonstrated.
%

\subsection*{Universality}

%
In the framework of universal systems, in which the two-body scattering length is divergent, the scattering volume of $n-^3H$ follows an identical pattern as before, but with a convergent value of $\sim4$ fm$^3$.
This can be compared to the typical coordinate scale of the system, which, in this case, is uniquely identifiable with the three-body scale $R_3=(-2mE_3/\hbar^2)^{-1/2}\simeq 6$ fm. 
We find that $(a_1)^{-1/3}/R_3 \simeq  1/4$, which is a small, but still natural ratio.

** here I have some discrepancies (martin A11 is twice Rimas A11)
\begin{figure}
\centering
\includegraphics[width=0.95\textwidth]{./Graphs/unitarityA} 
\caption{Temporary: unitary scattering lengths / volume}
\label{fig:Resonance_pole}
\end{figure}
**[martin pole and data for unitarity]**

\section{conclusion}

\bibliographystyle{ieeetr}
%elsarticle-harv}
\bibliography{bibi.bib}

\section{Appendix: Resonating group method and interactions}
\end{document}

### 2022-01-06 manuscript/Draft_0.2.tex
DC initial commit

--- 2022-01-06 manuscript/Draft_0.1.tex
@@
 
-\author{Johannes Kirscher}
-\address{Theoretical Physics Division, School of Physics and Astronomy,\\
-  The University of Manchester, Manchester, M13 9PL, UK}
-
-\author{Martin Sch{\"a}fer}
-\address{Nuclear Physics Institute of the Czech Academy of Sciences, 25069 \v{R}e\v{z}, Czech Republic}
-
-\author{Rimantas Lazauskas}
-\address{IPHC, IN2P3-CNRS/Universit\'e de Strasbourg BP 28, F-67037 Strasbourg Cedex 2, France}
-
 \author{Lorenzo Contessi}\email{lorenzo@contessi.net}
@@
 
+\author{Johannes Kirscher}
+\address{Theoretical Physics Division, School of Physics and Astronomy,\\
+  The University of Manchester, Manchester, M13 9PL, UK}
+
+\author{Rimantas Lazauskas}
+\address{IPHC, IN2P3-CNRS/Universit\'e de Strasbourg BP 28, F-67037 Strasbourg Cedex 2, France}
+
+\author{Martin Sch{\"a}fer}
+\address{Nuclear Physics Institute of the Czech Academy of Sciences, 25069 \v{R}e\v{z}, Czech Republic}
+
 \date{\today}
@@
 \begin{abstract} 
-(to be cleaned at the end)
-Few-body scattering resonances appear in multiple physical fields and are commonly found in experiments. 
-Compared with boundstates, they are more difficult to be studied theoretically and numerically because of their belonging to the continuum phase-space.
-In this study, we analyze the minimal theory that predicts the appearance of $L=1$ four-body resonance.
-This state is known in nuclear physics to be related to the lighter nucleus that shows resonant behavior: $^4$H.
-However, we aim not only to study it in the nuclear framework but also in more general universal systems.
-For this purpose, we employ a contact effective field theory both fitted on nuclear observables (pionless effective field theory) and to unitary systems (universal effective field theory).
-This study will help to understand how resonances emerge in few- and many-body systems for nuclear physics and any other physical field close to universality.
+Scattering resonances are ubiquitous in physics, and for the understanding of the behaviour of few-body quantum systems as important as bound states.
+Compared with the latter, their theoretical handling and their role in
+the interpretation of data is complicated through their unstable nature
+which is reflected in their wave functions not being elements of a
+square-integrable space.
+The smallest nuclear system comprised solely of resonances
+is 4-hydrogen with $L=1$ states about $3.5$~MeV above the triton-neutron
+threshold.
+
+In this article, we analyze the minimal contact theory which predicts
+such $P$-wave, four-body resonances. Furthermore, we establish numerically
+the emergence of this specific resonance pole for a wider class of systems
+whose two-body scale is significantly larger ($\to\infty$) compared with the
+interaction range.
+Specifically, we employ a contact effective field theory renormalized
+with nuclear observables -- in which case the interaction is identical
+to the leading order of the pionless effective field theory --
+and to unitary systems without a finite two-body scale (universal
+contact effective field theory). We find a negative-parity four-body
+resonance pole which is stable with respect to the short-distance structure
+of the regularized two- and three-body momentum-independent contact
+potentials with three independent numerical algorithms: a finite-volume
+Gaussian-stochastic-variational technique, the solution of the AGS on a
+discrete coordinate-space grid, and a one-channel, two-body,
+resonating-group reduction of the problem.
+Thereby we demonstrate that a zero-range potential
+provides a non-trivial pole structure for the four-body amplitude.
 \end{abstract}
@@
 
-Resonances are ever-present in quantum and classical physics.
-However, especially in many-particle quantum fields as hadronic, nuclear, and atomic physics, they are far from been trivial to be predicted and calculated. 
-A resonance in these fields is generally a consequence of a nonperturbative and complex interplay of particle-particle interactions and open channels that leads to the existence of multiple excitation and thresholds.
-The broad size and many-body nature make these states also relatively hard to be identified experimentally. 
-Although many models predict the existence of resonant states with better or worse success, just looking at the Hamiltonian of a system it is hard to foresee their existence, and the numerical methods that can extract complex energy are, in general, expensive or less accurate than the ones developed for bound states.
+Resonance phenomena occur ubiquitously in quantum and classical physics.
+Relative to stable bound states, their handling in many-particle hadronic, nuclear,
+and atomic physics is complicated. 
+A resonance results from a nonperturbative interplay of particle-particle interactions,
+fine-tuned potential shapes, and channel couplings that lead to multiple
+excitations and thresholds.
+Relative long life times and energies very close to production thresholds lead to
+clean, measurable signals, while in practise, a rapid decay and an energy far from
+threshold makes their identification with cross section data involved. 
+Theoretically, the structure of a Hamiltonian usually does not expose the existence of
+resonances without explicitly solving dynamical equations. In the latter course,
+numerical methods to extract complex energies are, in general, expensive and
+less accurate compared with those for bound states.
 %
@@
 %
-Among nuclear systems with resonances, $^4$H $J^\pi=1^-$ has a special role and has been object of several studies as it is known to be the smallest nucleus with a (relatively broad) resonance.
+In order to identify general features of an interaction which allow for the
+prediction of resonances, we focus on the smallest nuclear system, known to
+be characterized by a resonance, namely, the 4-hydrogen ($^4$H).
+In this system, $J^\pi=0^-, 1^-, 2^-$ resonances are found experimentally approcimately
+$5.2$~MeV, $3.5$~MeV, and $3.2$~MeV, respectively, above the triton-neutron threshold.
+Cross sections and scattering parameters have been studied extensively both experimentally
+~\cite{osti_4230875, Phillips:1980zz, Tilley:1992zz}~and theoretically~
+\cite{Ciesielski:1997vy,Ciesielski:1998sy,Ciesielski:1999pp,Viviani:1998gr,Fonseca:1999zz,Lazauskas:2004uq}.
+The position of the $^4$H, $J^\pi=1^-$ resonance pole was located in
+Refs.~\cite{Arai:2003ek,deDiego:2007rd,Lazauskas:2019cxj}~ at an energy
+$Re(E)=\{0.90 - 1.23\}$~MeV and width $\Gamma=\{3.5 - 5.8\}$~MeV.
+From data, a $R$-matrix analysis puts this pole at $Re(E)=3.50$~MeV and $\Gamma=6.73$~MeV~
+\cite{Tilley:1992zz}.
+Despite this discrepancy, the sheer existence of the pole is remarkable.
 %
-In particular, cross-sections and scattering parameters have been studied extensively experimentally (e.g. \cite{osti_4230875, Phillips:1980zz, Tilley:1992zz}) and theoretically.
-Concerning the theoretical side, several interactions and different numerical methods have been tested
-(see, e.g. \cite{Ciesielski:1997vy,Ciesielski:1998sy,Ciesielski:1999pp,Viviani:1998gr,Fonseca:1999zz,Lazauskas:2004uq}) to predict well phaseshifts especially for low-energy scattering.
 %
-Fewer studies can be found, instead, about the position of the $^4$H resonance pole that induces such phaseshift. 
-In \cite{Arai:2003ek,deDiego:2007rd,Lazauskas:2019cxj} the resonance position of $^4$H is extracted using respectively, RGM (which will be explained in the next sections of this paper), two-body $n-t$ potential, and three microscopic potentials with a Faddeev-Yakubovsky solver.
-The theoretical models agree for the presence of a $J^\pi=1^-$ resonance pole with energy $Re(E)=\{0.90 - 1.23\}$ MeV and width $\Gamma=\{3.5 - 5.8\}$ MeV.
-Experimentally, the resonant pole can be extracted by R-matrix analysis to be at $Re(E)=3.50$ MeV and  $\Gamma=6.73$ MeV \cite{Tilley:1992zz}.
-Although there is no precise agreement among experiment and models on the energy position of this resonant pole, the ability to create it in such models is still remarkable and has intrinsic value in the interpretation of the experimental cross-section.
 %
-The importance of studying $^4$H resonances and of the theoretical mechanisms that create it exceed the description of the system itself. 
-It is the getaway for larger systems: on one hand for many-neutrons, on the direction of studying the stability of neutron tears and eventually to the neutron star equation of state.
-On the other hand, to the study of resonances in heavy nuclei that are nowadays still hard or even impossible from ab-initio principles. 
+Why does
+such a pole emerge in the four-body amplitude but is absent, e.g., in the
+deuteron-neutron quartet channel or the three-neutron system? What are minimal
+conditions and characteristics of the employed models necessary for these features?
+These questions are crucial in the development of the nuclear effective field
+theory in order to make it useful for the description of heavier nuclei beyond
+the $S$ shell.
+Furthermore, fermi statistics which enforces higher relative angular
+momenta in ground-state wave functions of more than four nucleons, is equally
+relevant for hadronic, atomic, in general, all fermions amenable
+to a description with zero-range forces. Hence, an understanding how the structure
+of these forces leads to certain few-body resonance poles carries value far beyond the
+$^4$H system, namely: is a leading-order description of a system of particles, whose
+statistics demand mixed-orbital-symmetry states, with properly renormalized coupling
+strengths of zero-range, possibly spin-/flavour-dependent interactions possible?
+%In this study, we are interested in both these aspects on the framework of very minimalists nuclear forces: renormalizable contact effective field theories. 
 %
-In this study, we are interested in both these aspects on the framework of very minimalists nuclear forces: renormalizable contact effective field theories. 
+%
+%
 %
@@
 %
-In the last years, effective field theories (EFT) have had an ever-increasing impact on nuclear and atomic physics. 
-They rely on the expansion of the appropriate underline theory onto a set of operators hierarchically arranged in a powercounting. 
-The origin of this expansion depends on the kind of system in study and of the interparticle typical momentum exchanged, and differentiate an EFT from another. 
-For example, it was shown that few-body nuclear systems are close to the unitary limit, in which the two-body scattering length is much larger than any other scale in such systems, allowing the description of few nucleons expanding the EFT around an infinite (or large) scattering length (see \cite{vanKolck:1999mw}).
-This takes the name of pionless powercounting (\eftnopi) and, contrary to the chiral EFT, in which pions origin long-range forces, it is an expansion in contact operators.
-The absence of pions in \eftnopi limits this theory to be a low-momentum theory (i.e.
-can not describe phenomena which typical momentum would allow the creation of pions) but allows it to be fully renormalizable and relatively easy to be treated numerically and analytically.
-This makes it best suited to understand in simple terms even complex many-body phenomena and for the description of very shallow quantum states, like resonant poles. 
-In the last years, \eftnopi was proven to be a valuable theory to study the behavior of many-boson systems and nuclei up to four nucleons. 
-However, the LO of the theory does not appear to perform as well for the behavior of multi-fermionic systems, on which it erroneously predicts unbound nuclei above four particles (eg.
-$^7$Li and $^{16}$O) \cite{Schafer:2020ivj,Contessi:2017rww}.
-The reason for this is to be attributed to the theory's more general inability of creating bound mixed symmetry states.
-However, the subleading order of the EFT may still be able to correct this behavior provided that the LO creates, at least, an unbound state (virtual o resonant) that can be moved to the correct bound position.
-On the contrary, if no state is present at LO in these systems, of which $^4$H is the minimal representative, only a modification of the powercounting, and therefore of the entire theory, will allow for the correct description of nuclear physics using contact EFTs.
-The creation of resonant poles in LO \eftnopi is possible, as it was shown in $nn\Lambda$ systems \cite{Schafer:2020rba} (as a subthreshold resonance), however, there is no record of such poles created in systems with mixed symmetry groundstates as $^4$H.
-By approaching the existence of a resonant pole in $^4$H we are tackling two problems at the same time: the possibility of creating resonances with the barest possible interaction and the fact that contact EFT can or not describe nuclear physics.
-%
+Such renormalizable effective field theories (EFT) were instrumental in understanding
+the relation between nuclear physics and its underlying theory of quantum chromodynamics
+and for deriving universal features which nuclei share with atoms.
+All EFT's comprise of the most general Lagrangean whose terms are built with
+appropriately chosen degrees of freedom and meet certain internal and space-time symmetries.
+A hierarchy (power counting) amongst this infinity of operators and their weight within
+an iterative expansion of the $S$-matrix renders the theory {\it effective}, i.e., useful.
+In the two-body sector, the convergence of the expansion and the choice of the relevant
+degrees of freedom depends on the typical momentum exchanged between interaction partners;
+for different typical momenta, different EFT expansions are needed. 
+For instance, few-body nuclear systems are close to the unitary limit, where the two-body
+scattering length is much larger than any other scale, an
+expansion around an infinite (or large) scattering length with solely nuclear degrees of freedom
+yields the bulk structure of nuclei up to 4-helium~\cite{vanKolck:1999mw}.
+For momenta that allow for the creation of pions, this pion-less power counting (\eftnopi)
+fails. For these momenta, chiral EFTs couple the pion field to the nucleons and thereby
+introduce long-range forces at leading order, while \eftnopi~is of zero-range at
+leading order and thus easier to treat numerically and analytically.
+Whether this simplicity of a zero-range theory still does not lead to an exclusion
+of complex many-body phenomena, e.g., shallow quantum states and resonance poles is
+unknown and shall be studied in this article.
 
-%
-To access this state we first fix a \eftnopi on nuclear observables (fixing the nucleon mass, and the deuterium and triton bindings).
-The same theory was also fixed to nuclear systems in which the two-body potential was tuned to the unitary limit.
-This last case allows access to the universal limit and the deviation of the nuclear potential from it.
-We chose to use a SU(4) symmetric theory in both cases for simplicity as this was proven to be a good first-order representation of nuclear physics \cite{Konig:2016utl}.
+What is known about \eftnopi, in particular, is its ability to predict the behavior
+of many-boson systems and nuclei up to four nucleons. 
+However, the leading order (LO) of the theory cannot account for the observed behavior of
+multi-fermionic systems. There, it erroneously predicts unbound nuclei above four
+particles, e.g.~$^7$Li and $^{16}$O~\cite{Schafer:2020ivj,Contessi:2017rww}.
+It was conjectured more generally, that zero-range theories cannot sustain 
+bound states of mixed symmetry.
+However, the bound character of a state might appear only at a higher orders of the EFT
+provided that the LO creates a pole of other kind, virtual or resonant, which the
+modification of the interaction at higher order transforms into a bound state. 
+If no such pole is present at LO in these systems -- of which $^4$H is the smallest --
+only a modification of the power counting
+will furnish the correct description of nuclear physics with contact EFTs.
+
+The creation of resonant $S$-wave poles at LO \eftnopi~was demonstrated in case of the
+hyper triton ($nn\Lambda$) in Ref.~\cite{Schafer:2020rba} (as a subthreshold resonance) but
+there is no record of such poles being created renormalization-scheme independently
+in systems with mixed symmetry ground states
+such as $^4$H with a zero-range theory. 
+It is the aim of this work to analyze this creation of a four-body $P$-wave resonance
+pole from an zero-range, spherically-symmetric regularized contact interaction with
+coupling strengths resembling nuclear systems close to unitarity and also systems which
+realize this limit with an infinite two-body scattering length, i.e., zero-energy bound
+state.
+
+In the following section, we introduce the Hamiltonian of the theory along with
+comments on its solution with a Gaussian-stochastic-variational method, the
+treatment of the scattering problem via the Alt, Grassberger, and Sandhas equations
+in coordinate space, and the reduction of $N$-body, two-fragment scattering onto a
+two-body problem.
+Following this, we present results for effective-range parameters and pole positions
+for the low-energy scattering of a neutron on $^3$H before generalizing this to a
+generic point particle impinging on a universal trimer.
+Finally, we relate the regulator independence of the results to the deployed minimal
+theory as a first-order approximation of nuclei and universal, unitary systems.
 
@@
 \end{table}
+
+The minimal theory for the
 

### 2022-01-06 manuscript/Draft_0.3.tex
DC initial commit

--- 2022-01-06 manuscript/Draft_0.2.tex
@@
 Scattering resonances are ubiquitous in physics, and for the understanding of the behaviour of few-body quantum systems as important as bound states.
-Compared with the latter, their theoretical handling and their role in
-the interpretation of data is complicated through their unstable nature
-which is reflected in their wave functions not being elements of a
-square-integrable space.
-The smallest nuclear system comprised solely of resonances
-is 4-hydrogen with $L=1$ states about $3.5$~MeV above the triton-neutron
+Compared with the latter, their theoretical handling and their role in the interpretation of data is complicated through their unstable nature which is reflected in their belonging to the continuum spectrum.
+The smallest nuclear system comprised solely of resonances is 4-hydrogen with $L=1$ states about $3.5$~MeV above the triton-neutron
 threshold.
@@
 the emergence of this specific resonance pole for a wider class of systems
-whose two-body scale is significantly larger ($\to\infty$) compared with the
-interaction range.
+whose two-body scale is significantly larger ($\to\infty$) than their interaction range.
 Specifically, we employ a contact effective field theory renormalized
-with nuclear observables -- in which case the interaction is identical
-to the leading order of the pionless effective field theory --
+with nuclear observables (LO pionless effective field theory)
 and to unitary systems without a finite two-body scale (universal
@@
 In order to identify general features of an interaction which allow for the
-prediction of resonances, we focus on the smallest nuclear system, known to
-be characterized by a resonance, namely, the 4-hydrogen ($^4$H).
-In this system, $J^\pi=0^-, 1^-, 2^-$ resonances are found experimentally approcimately
+prediction of resonances, we focus on  the 4-hydrogen ($^4$H), the smallest nuclear system known to
+be characterized by a resonance.
+In this system, $J^\pi=0^-, 1^-, 2^-$ resonances are found experimentally approximately
 $5.2$~MeV, $3.5$~MeV, and $3.2$~MeV, respectively, above the triton-neutron threshold.
@@
 \cite{Tilley:1992zz}.
-Despite this discrepancy, the sheer existence of the pole is remarkable.
+Despite the quantitative discrepancy among theory and experiment, the sheer existence of the pole in different models is remarkable.
 %
@@
 \section{Appendix: Resonating group method and interactions}
+In this section, we reformulate the $A$-body problem of one particle scattering elastically off
+an $(A-1)$-body bound state with a relative kinetic energy which is small relative to the lowest
+excitation energy of the target compound.
+
 \end{document}

### 2022-03-27 manuscript/Draft_0.3.tex
India V1

@@
 
-\usepackage{epsfig}
-\usepackage[utf8]{inputenc}
+\usepackage{graphicx} 
+\usepackage{dashrule}
+\usepackage{dcolumn} 
+\usepackage{longtable} 
+\usepackage{mathtools}
+\usepackage{amssymb} 
+\usepackage{bbold}
+\usepackage{amsmath} 
+\usepackage{amsfonts} 
+\usepackage{wasysym}
+\usepackage{slashed} 
 \usepackage[dvipsnames]{xcolor} 
-\usepackage[normalem]{ulem}
-%\usepackage{slashed}
-\usepackage{caption}
-\usepackage{amssymb}
-\usepackage{mathtools}
-\usepackage{bbold}
-\usepackage{amssymb,latexsym}
-\usepackage{amsmath,amsbsy,bbm}
+\usepackage{soul}
+\usepackage{rotating}
+\usepackage{paracol}
+\usepackage{nicefrac}
+\usepackage{MnSymbol}
 
@@
 
+\newcommand{\eg}{\textit{e.g.}~}
+\newcommand{\ie}{\textit{i.e.}~}
+\newcommand{\viz}{\textit{viz.}~}
+\newcommand{\cf}{\textit{cf.}~}
 \newcommand{\eftnopi}{\mbox{EFT$(\not \! \pi)$}}
+\newcommand{\ve}[1]{\ensuremath{\boldsymbol{#1}}}
+\newcommand{\rcm}{\ensuremath{\ve{R}_\text{\scriptsize{c.m.}}}}
+\newcommand*{\mprime}{^{\prime}\mkern-1.2mu}
+\newcommand*{\mdprime}{^{\prime\prime}\mkern-1.2mu}
+\newcommand*{\mtprime}{^{\prime\prime\prime}\mkern-1.2mu}
+\newcommand{\ddrei}[1]{\delta_{\tiny \lambda}^{(3)}\!\big(#1\big)}
+\newcommand{\cc}{\ensuremath C(\lambda)}
+\newcommand{\dd}{\ensuremath D(\lambda)}
+
+\newcommand{\bra}[1] {\left\langle~#1~\right|}
+\newcommand{\ket}[1] {\left|~#1~\right\rangle}
+\newcommand{\bet}[1] {\left|#1\right|}
+\newcommand{\overlap}[2] {\left\langle\,#1\,\left|\,#2\,\right.\right\rangle}
+\newcommand{\me}[3] {\left\langle\,#1\,\left.\left|\,#2\,\right|\right.\,#3\,\right\rangle}
+\newcommand{\mer}[3] {\left\langle\,#1\,\left|\left.\,#2\,\right|\,#3\,\right.\right\rangle_{\ve{R}}}
+\newcommand{\redme}[3] {\left\langle\,#1\,\middle|\right|\,#2\,\left|\middle|\,#3\,\right\rangle}
 
@@
 \section{Appendix: Resonating group method and interactions}
-In this section, we reformulate the $A$-body problem of one particle scattering elastically off
-an $(A-1)$-body bound state with a relative kinetic energy which is small relative to the lowest
-excitation energy of the target compound.
+
+%We treat $A$ as the triton, $B$ as the neutron, and expand the cluster-internal function in a Gaussian basis
+%
+%\begin{equation}\label{eq.app.trit}
+%\phi_3=\sum_n^{N_f}\,c_n\cdot e^{-\alpha_n\sum_{i=1}^{3}\left(\ve{r}_i-\ve{R}_3\right)^2}
+%\qquad
+%\begin{array}{ll}
+%     N_f      & \text{\small : basis dimension}  \\
+%     \ve{r}_i & \text{\small : single-particle coordinates}  \\
+%     \ve{R}_3 & \text{\small : center of mass of the triton fragment}
+%\end{array} 
+%\quad,
+%\end{equation}
+%
+%to allow for an analytical reduction of the equation of motion from its full four-body to an
+%effective two-body version which assumes that the triton-internal motion is unaffected by the
+%scattered neutron.
+%
+% As we treat the triton as inert, we consider
+
+The non-relativistic dynamics of the four particles is given by the solutions to
+
+\begin{equation}\label{eq.rgm.eqom}
+\left(-\frac{\hbar^2}{2\mu}\ve{\Delta}_R-E+\mathcal{V}\right)\ket{\Psi}
+~
+\Leftrightarrow
+~
+\me{\delta\Psi}{\hat{H}-E}{\Psi}
+=
+0
+\qquad.
+\end{equation}
+
+The second, viz. the projection/variational equation is equivalent to the Schr\"odinger equation if
+$\delta\Psi$ denotes an arbitrary variation of the state.
+The resonating-group methods expresses the total wave function of this state in the form
+
+\begin{eqnarray}\label{eq.app.rgmwfkt}
+\Psi
+&=&
+\mathcal{A}\Big\lbrace
+\sum_i\phi(A_i)\,\phi(B_i)\,\chi_i(\ve{R}_i)
+\nonumber\\
+&&
++\sum_j\phi(A_j)\,\phi(B_j)\,\phi(C_j)\,\chi_j(\ve{R}_{j1},\ve{R}_{j2})
++\sum_k\phi(A_k)\,\phi(B_k)\,\phi(C_k)\,\phi(D_k)\,\chi_j(\ve{R}_{k1},\ve{R}_{k2},\ve{R}_{k3})
+\nonumber\\
+&&
++\ldots+\sum_mc_m\eta_m
+\Big\rbrace~
+\zeta(\rcm)
+\qquad,
+\end{eqnarray}
+
+where each term corresponds to a particular fragmentation of the particles into two, three, four, $\ldots$ cluster.
+The internal motion of such a cluster of $A$ particles is expanded with a complete set of functions $\phi(A_i)$, and the
+relative motion between the clusters is encoded in the $\chi_i$'s. The last term is included to improve the expansion if the
+fragment-internal basis is not complete and/or if the cluster expansion is truncated such that a more complicated shape
+of the state for small separations between the clusters cannot be accounted for.
+
+For the elastic scattering of a neutron off a three-nucleon targets whose ground state is 
+$\Delta\epsilon_\text{nuclear}\approx6.2~$MeV and
+$\Delta\epsilon_\text{unitary}\approx8.4~$MeV, respectively, below the lowest dissociation thresholds,
+and the relative energies between the fragments $E_r\ll\Delta\epsilon$,
+we chose to express the wave function of the system with a two-cluster, single-channel ansatz
+without specific distortion:
+
+\begin{equation}\label{eq.app.rgmwfkt2}
+\Psi
+=
+\mathcal{A}_{31}\left[\phi(3)\phi(1)\,\chi(\ve{R})\,\zeta(\rcm)\right]
+=
+\int\mathcal{A}_{31}\left[\phi(3)\phi(1)\,\delta\big(\ve{R}-\ve{R}\mprime\big)\,\zeta(\rcm)\right]\,\chi(\ve{R}\mprime)\,d\ve{R}\mprime
+\qquad.
+\end{equation}
+
+\cf\eqref{eq.app.rgmwfkt}, first term. The parameter representation employed with the second equality in \eqref{eq.app.rgmwfkt2}
+will yield a defining equation for the relative motion independent of the antisymmetrizer $\mathcal{A}$.
+Assuming an inert triton core allows solely for a variation of the relative wave function:
+
+\begin{equation}\label{eq.app.rgmwfkt}
+\delta\Psi
+=
+\int\,\delta\chi(\ve{R}\mprime)\,\mathcal{A}_{AB}\left[\phi_A\phi_B\,\delta\big(\ve{R}-\ve{R}\mprime\big)\,\zeta(\rcm)\right]\,d\ve{R}\mprime
+\equiv
+\sumint \delta a_n\Phi_n
+\qquad.
+\end{equation}
+
+The latter notation allows for the following concise form of the projection equation
+
+\begin{equation}\label{eq.app.rgmwfkt}
+\me{\sumint \delta a_m\Phi_m}{\hat{H}-E}{ \sumint a_n\Phi_n}=0
+~\to~\mer{\phi(3)}{\hat{H}-E}{\mathcal{A}_{31}\left[\chi(\ve{R}\mprime)\,\phi(3)\right]}=0
+\qquad
+\end{equation}
+
+where the {\it ket} subscript average indicates that the average over the relative radius was already taken,
+and the remaining integrals are over the fragment-internal coordinates. If the cluster-internal states are properly
+anti-symmetrized, it remains to consider the inter-fragment anti-symmetrization via
+ $\mathcal{A}_{31}=\mathbb{1}-\hat{P}_{14}$.
+We chose nucleons 1 and 4 to be the neutrons with identical spin orientation, and hence need to consider the permutation of
+those particles, only. All other permutations $\hat{P}_{ij}$ will yield zero matrix elements because of the orthogonality of
+the internal states.
+
+Being more explicit, the motion of the two fragments relative to each other is approximated by
+\begin{equation}\label{eq.rgm.eqom}
+\int\left\lbrace~\phi(3)\left(-\frac{\hbar^2}{2\mu}\ve{\Delta}_R-E+B(3)+\mathcal{V}_{31}\right)
+\mathcal{A}_{31}\left[\phi(3)\,\chi(\ve{R})\right]\right\rbrace d\ve{r}_{1,2,3}=0
+\qquad.
+\end{equation}
+
+Employing the parameter representation, $\chi(\ve{R})=\int\delta(\ve{R}-\ve{R}\mprime)\chi{\ve{R}\mprime}d\ve{R}\mprime$,
+and expanding the triton ground state in Gaussians,
+$\phi(3)=\sum_n^{N_f}\,c_n\cdot e^{-\alpha_n\sum_{i=1}^{N_A}\left(\ve{r}_i-\ve{R}_3\right)^2}$,
+in combination with the leading-order \eftnopi~potential
+
+\begin{equation}\label{eq.app.pot}
+\mathcal{V}_{31}=\cc\,\sum_{i\in A\atop j\in B}\,\ddrei{\ve{r}_i-\ve{r}_j}+
+\dd\,\sum_{i,j,k\atop i\in A\Rightarrow j\vee k\in B}\ddrei{\ve{r}_i-\ve{r}_j}\,\ddrei{\ve{r}_i-\ve{r}_k}
+\end{equation}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.95\textwidth]{./Graphs/rgm_potential} 
+\caption{Two-fragment potential as a function of the distance between a
+neutron and the center of mass of a triton. The plot shows the $P$-wave component of the
+interaction including local and non-local part of the kinetic-, pair-, and three-body interactions.
+The non-local parts are evaluated at $\rho=\rho'$}
+\label{fig:rgm_potential}
+\end{figure}
 

### 2022-03-28 manuscript/Draft_0.3.tex
India V2 -- plots added to manuscript

@@
 \usepackage{dcolumn} 
-\usepackage{longtable} 
 \usepackage{mathtools}
@@
 \usepackage{MnSymbol}
+\usepackage{caption}
 
@@
 
+\newcommand{\figref}[1]{fig.~(\ref{#1})}
+\newcommand{\tabref}[1]{table~(\ref{#1})}
+\newcommand{\eref}[1]{eq.~(\ref{#1})}
 \newcommand{\eg}{\textit{e.g.}~}
@@
 \newcommand{\cf}{\textit{cf.}~}
-\newcommand{\eftnopi}{\mbox{EFT$(\not \! \pi)$}}
+\newcommand{\eftnopi}{\mbox{EFT($\slashed{\pi}$) }} 
 \newcommand{\ve}[1]{\ensuremath{\boldsymbol{#1}}}
@@
 \newcommand{\dd}{\ensuremath D(\lambda)}
+\newcommand{\hbstwom}{\ensuremath \frac{\hbar^2}{2\mu}}
+\newcommand{\twomhbs}{\ensuremath \frac{2\mu}{\hbar^2}}
+\newcommand{\coup}[3]{\left[\,#1\,\otimes\,#2\,\right]^{#3}}
+\newcommand{\threej}[6]{ \begin{pmatrix}
+   #1 & #2 & #3 \\
+   #4 & #5 & #6 
+  \end{pmatrix}}
 
@@
 
-\cf\eqref{eq.app.rgmwfkt}, first term. The parameter representation employed with the second equality in \eqref{eq.app.rgmwfkt2}
+\cf\eref{eq.app.rgmwfkt}, first term. The parameter representation employed with the second equality in \eref{eq.app.rgmwfkt2}
 will yield a defining equation for the relative motion independent of the antisymmetrizer $\mathcal{A}$.
@@
 
-Employing the parameter representation, $\chi(\ve{R})=\int\delta(\ve{R}-\ve{R}\mprime)\chi{\ve{R}\mprime}d\ve{R}\mprime$,
-and expanding the triton ground state in Gaussians,
-$\phi(3)=\sum_n^{N_f}\,c_n\cdot e^{-\alpha_n\sum_{i=1}^{N_A}\left(\ve{r}_i-\ve{R}_3\right)^2}$,
-in combination with the leading-order \eftnopi~potential
+This expression is further evaluated by:
+(i)~employing the parameter representation, $\chi(\ve{R})=\int\delta(\ve{R}-\ve{R}\mprime)\chi(\ve{R}\mprime)d\ve{R}\mprime$;
+(ii)~expanding the triton ground state in Gaussians,
+$\phi(3)=\sum_n^{N_f}\,c_n\cdot e^{-\alpha_n\sum_{i=1}^3\left(\ve{r}_i-\ve{R}_3\right)^2}$ with norm
+$\mathbb{N}_3=\sum_{i,j=1}^{N_f}c_ic_j\left(\frac{\pi}{\alpha_i+\alpha_j}\right)^{\nicefrac{3}{2}}$;
+(iii)~substituting the leading-order \eftnopi~potential as inter-cluster interaction,
 
-\begin{equation}\label{eq.app.pot}
-\mathcal{V}_{31}=\cc\,\sum_{i\in A\atop j\in B}\,\ddrei{\ve{r}_i-\ve{r}_j}+
+\begin{eqnarray}\label{eq.app.pot}
+\mathcal{V}_{31}
+&=&
+\cc\,\sum_{i\in A\atop j\in B}\,\ddrei{\ve{r}_i-\ve{r}_j}+
 \dd\,\sum_{i,j,k\atop i\in A\Rightarrow j\vee k\in B}\ddrei{\ve{r}_i-\ve{r}_j}\,\ddrei{\ve{r}_i-\ve{r}_k}
+\nonumber\\
+&=&
+\cc\cdot\left(\ddrei{\ve{r}_2-\ve{r}_4}+\ddrei{\ve{r}_3-\ve{r}_4}\right)
++\dd\cdot\left(\ddrei{\ve{r}_2-\ve{r}_3}\,\ddrei{\ve{r}_2-\ve{r}_4}\right)
+\qquad;
+\end{eqnarray}
+
+(iv)~performing the action of $\mathcal{A}_{31}$ on $\phi_3$ and $\delta(\ve{R}-\ve{R}\mprime)$;
+and finally, (v)~doing the Gaussian integrals for the triton-internal single-particle coordinates $\ve{r}_{1,2,3}$.
+Thereby, one obtains the form
+
+\begin{equation}\label{eq.app.rgmform}
+(\hat{T}-E)~\chi(\ve{R})+\mathcal{V}^{(1)}(\ve{R})~\chi(\ve{R})+
+\int d^{(3)}\ve{R}\mprime~\mathcal{V}^{(2)}(\ve{R},\ve{R}\mprime,E)~\chi(\ve{R}\mprime)=0
+\qquad.
+\end{equation}
+
+More conveniently, we do express this equation as
+
+\begin{gather}\label{eq.app.rgm.sglnonloc}
+\mathbb{N}_3\cdot\left(-\ve{\Delta}_R-\ve{p}^2\right)\,\chi(\ve{R})+
+\sum_{i,j=1}^{N_f}c_ic_j\left[
+\sum_{n=1}^{2}\eta^{(ij)}_n~e^{-w^{(ij)}_n\ve{R}^2}\chi(\ve{R})-
+\sum_{n=1}^{3}\int\left\lbrace\zeta^{(ij)}_n\hat{\zeta}_n\,e^{-a^{(ij)}_n\ve{R}^2-b^{(ij)}_n\ve{R}\cdot\ve{R}'-c^{(ij)}_n\ve{R}'^2}\right\rbrace\chi(\ve{R}') d\ve{R}'
+\right]
+=0
+\\
+\intertext{with $\hat{\eta}_n,\hat{\zeta}_n,w_n,a_n,b_n,c_n$ dependent upon,
+(i) the low-energy constants: $\cc,\dd$, (ii) the triton-expansion parameters: $\alpha_n, c_n$,
+(iii) the regulator parameter: $\lambda$, and (iv) the relative momentum: $\ve{p}^2=2\mu E$, as given in \tabref{tab.app.pot.coffs}.\nonumber} 
+\end{gather}
+
+\setlength{\tabcolsep}{4pt}
+\renewcommand{\arraystretch}{1.6}
+\begin{table}
+\begin{tabular}{l|c|c|c|c}
+$n$ & $\eta^{(ij)}$  & $w^{(ij)}$ & & \\\hline
+1   & $\frac{2\cc}{\left[2(\alpha_i+\alpha_j)(3\alpha_i+3\alpha_j+2\lambda)\right]^{\nicefrac{3}{2}}}$ & 
+      $\frac{3(\alpha_i+\alpha_j)\lambda}{3(\alpha_i+\alpha_j)+2\lambda}$ &  &  \\
+2   & $\frac{\dd}{\left[6(\alpha_i+\alpha_j)^2+16\lambda(\alpha_i+\alpha_j)+2\lambda^2\right]^{\nicefrac{3}{2}}}$ & 
+      $\frac{3(\alpha_i+\alpha_j)\lambda((\alpha_i+\alpha_j)+2\lambda)}{3(\alpha_i+\alpha_j)^2+8(\alpha_i+\alpha_j)\lambda+\lambda^2}$ &  &  \\
+\hline\hline
+           & $\zeta^{(ij)}\otimes\hat{\zeta}$ & $a^{(ij)}$ & $b^{(ij)}$ & $c^{(ij)}$ \\\hline
+1   & $\hbstwom\frac{3^3}{2^6}~\frac{1}{\left[2(\alpha_i+\alpha_j)\right]^{\nicefrac{3}{2}}}\otimes\left(-\ve{\Delta}_R-\ve{p}^2\right)$ &
+      $\frac{3}{32}(\alpha_i+9\alpha_j)$ & 
+      $\frac{9}{16}(\alpha_i+\alpha_j)$ & 
+      $\frac{3}{32}(9\alpha_i+\alpha_j)$ \\
+2   & $-\frac{3^3}{2^5}~\frac{\cc}{\left[2(\alpha_i+\alpha_j)+\lambda\right]^{\nicefrac{3}{2}}}\otimes\mathbb{1}$ & 
+      $\frac{3(\alpha_i^2+9\alpha_j^2+10\alpha_i\alpha_j+\lambda(14\alpha_i+18\alpha_j))}{16(2(\alpha_i+\alpha_j)+\lambda)}$ & 
+      $\frac{18(\alpha_i+\alpha_j)(\alpha_i+\alpha_j)+2\lambda}{16(2(\alpha_i+\alpha_j)+\lambda)}$ & 
+      $\frac{3(9\alpha_i^2+\alpha_j^2+10\alpha_i\alpha_j+\lambda(6\alpha_i+2\alpha_j))}{16(2(\alpha_i+\alpha_j)+\lambda)}$  \\
+3   & $-\frac{3^3}{2^6}~\frac{\dd}{\left[2(\alpha_i+\alpha_j)+5\lambda\right]^{\nicefrac{3}{2}}}\otimes\mathbb{1}$ & 
+      $\frac{3(\alpha_i^2+9\alpha_j^2+10\alpha_i\alpha_j+\lambda(16\alpha_i+36\alpha_j)+27\lambda^2)}{16(2(\alpha_i+\alpha_j)+5\lambda)}$ & 
+      $\frac{18((\alpha_i+\alpha_j)^2+4\lambda(\alpha_i+\alpha_j)+3\lambda^2)}{16(2(\alpha_i+\alpha_j)+5\lambda)}$ & 
+      $\frac{3(9\alpha_i^2+\alpha_j^2+10\alpha_i\alpha_j+\lambda(24\alpha_i+4\alpha_j)+3\lambda^2)}{16(2(\alpha_i+\alpha_j)+5\lambda)}$  \\
+\hline\hline
+\end{tabular}
+\caption{\small{Local ($\eta,w$) and non-local ($\zeta,a,b,c$) components of the resonating-group \eref{eq.app.rgm.sglnonloc}.}}
+\label{tab.app.pot.coffs}
+\end{table}
+
+The character of the interaction is expected to depend strongly on the spatial symmetry of the wave function, and as
+the parities of the triton core and the point neutron are positive, the overall parity is set by the relative motion
+$\chi$. In order to investigate the parity dependence, we project into partial waves:
+Expanding $\chi(\ve{R})=R^{-1}\sum_{lm}\phi_{lm}(R)Y_{lm}(\hat{\ve{R}})$
+and projecting from the left with
+$R\,\int d^2\hat{\ve{R}}~Y^*_{lm}(\hat{\ve{R}})$
+before substituting
+$$
+e^{-b\ve{R}\cdot\ve{R}'}=4\pi\sum_{LM}i^Lj_L(ib RR')Y^*_{LM}(\hat{\ve{R}})Y_{LM}(\hat{\ve{R}}')\;\;;\;\;
+\ve{R}\cdot\ve{R}'=-\sqrt{3}\coup{\ve{R}_p}{\ve{R}\mprime_{-p}}{00}=\frac{4\pi}{3}RR'\sum_p(-)^p\,Y_{1p}Y'_{1-p}
+$$
+and $\ve{r}_m=\sqrt{\frac{4\pi}{3}}rY_{1,m}(\hat{\ve{r}})$
+yields
+\begin{align}
+0~=&
+~\mathbb{N}_3\cdot\left(\partial^2_R-\frac{l(l+1)}{R^2}+\ve{p}^2\right)
+\phi_{lm}(R)
+-
+\twomhbs\sum_{i,j=1}^{N_f}c_ic_j\Bigg(
+\sum_{n=1}^2\eta^{(ij)}_n~e^{-w^{(ij)}_nR^2}\phi_{lm}(R)\nonumber\\
+%
+&-\int dR\mprime~\phi_{lm}(R\mprime)~(4\pi RR\mprime )~\Bigg[
+%
+~\zeta^{(ij)}_1 \cdot e^{-a^{(ij)}_1R^2-c^{(ij)}_1R'^2}\cdot\Bigg\lbrace
+\left[-(4(a^{(ij)}_1)^2R^2+(b^{(ij)}_1)^2R\mprime^2-2a^{(ij)}_1)+\frac{l(l+1)}{R^2}-\frac{2\mu}{\hbar^2}E\right]
+ i^l j_{l}(ib^{(ij)}_1 RR')\nonumber\\
+%
+&-(4a^{(ij)}_1b^{(ij)}_1)\cdot RR\mprime\cdot
+\sum_Li^Lj_L(ib^{(ij)}_1 RR')~\hat{L}~\hat{l}~\threej{L}{1}{l}{0}{0}{0}^2~\triangle_{L1l}\Bigg\rbrace
+%
++\sum_{n=2}^3\zeta^{(ij)}_n\,i^l j_l(ib_n RR')\cdot 
+e^{-a^{(ij)}_nR^2-c^{(ij)}_nR'^2}~\Bigg]\Bigg)\label{eq.app.sglnonloc.pw.l.noloc}
+\end{align}
+with a 3-$j$ symbol $\neq0\Leftrightarrow L+1+l=$~even, and $\triangle_{j_1j_2j_3}\neq0\Leftrightarrow j_3=|j_1-j_2|,\ldots,j_1+j_2$.
+From this equation, we obtain solutions for $S$- and $P$-waves on a discrete, equidistant coordinate grid:
+$R,R\mprime\in\lbrace r_0,r_0+\epsilon,r_0+2\epsilon,\ldots,,\underbrace{r_0+N_\text{\tiny grid}\epsilon}_{=:r_{N_\text{\tiny grid}+1}}\rbrace$.
+We chose a maximal grid dimension such that for $R(\mprime)=r_{N_\text{\tiny grid}+1}$ both local and non-local interactions
+vanish. Thence, we solve \eref{eq.app.sglnonloc.pw.l.noloc} for the {\it principal-value} wave function ($\phi^{(P)}$)
+with the boundary condition
+
+\begin{eqnarray}\label{eq.app.principal.value.wfkt}
+\phi_{l,p}^{(P)}(R)
+&
+\stackrel{R\to\infty}{\simeq}
+&
+\sin\left(pR-\frac{\pi l}{2}\right)
++
+K_l
+\cdot
+\cos\left(pR-\frac{\pi l}{2}\right)\\
+&
+=
+&
+\lim_{pR\to\infty}\left[u_l(pR)\right]
++
+\tan\delta_l
+\cdot
+\lim_{pR\to\infty}\left[v_l(pR)\right]
+=
+\left\lbrace
+\begin{array}{ll}
+l=0:& \sin\left(pR\right)-\tan\delta_l\cos\left(pR\right)\\
+l=1:& \frac{\sin\left(pR\right)}{pR}-\cos\left(pR\right)-\tan\delta_l\left[\frac{\cos\left(pR\right)}{pR}+\sin\left(pR\right)\right]
+\end{array}
+\right.
+\;\;.
+\quad
+\end{eqnarray}
+
+For the Riccati-Bessel, $u_l(z)=zj_l(z)$, and the Riccati-Neumann Functions, $v_l(z)=zn_l(z)$, we use
+\cite{}~as reference, where $j_l(n_l)$ is the proper spherical Bessel(Neumann) function. Note, the relation
+between the Neumann and the spherical Bessel function of the second kind: $n_l(z)=(-)^ly_l(z)$.
+Now, we obtain the phase shifts from
+
+\begin{equation}\label{eq.app.phases}
+\tan\delta_l=\frac{\phi_{l,p}^{(P)}(r_{N_\text{\tiny grid}+1})}{v_l(pr_{N_\text{\tiny grid}+1})}-
+\frac{u_l(pr_{N_\text{\tiny grid}+1})}{v_l(pr_{N_\text{\tiny grid}+1})}
+\qquad.
 \end{equation}
@@
 interaction including local and non-local part of the kinetic-, pair-, and three-body interactions.
-The non-local parts are evaluated at $\rho=\rho'$}
+The non-local parts are evaluated at $R=R'$. The height of the potential's barrier shrinks continuously from
+the smallest cutoff (fat blue) to the largest (red), with intermediate values represented by green, dashed curves.}
 \label{fig:rgm_potential}
@@
 
+\begin{figure*}[th]
+\captionsetup{width=.4\linewidth,justification=raggedright}
+\begin{tabular}{cc}
+\begin{minipage}[t]{0.45\linewidth}
+ \includegraphics[width=\textwidth]{./Graphs/rgm_potential_MinMax}
+ \caption{Locus of the valley (red, dashed) and the barrier (blue, solid) of the effective resonating-group
+ interaction (\figref{fig:rgm_potential}) as a function of the regulator parameter $\lambda$.}
+\label{fig:rgm_pot_minmax}
+\end{minipage}
+&
+\begin{minipage}[t]{0.45\linewidth}
+ \includegraphics[width=\textwidth]{./Graphs/rgm_potential_DeltaMinMax}
+\caption{Regulator dependence of the difference between the first local maximum of the effective resonating-group potential
+(\figref{fig:rgm_potential}) and its first local minimum.}
+\label{fig:rgm_pot_valbardiff}
+\end{minipage}
+\end{tabular}
+\end{figure*}
+
 \end{document}

### 2022-05-26 manuscript/Draft_0.3.tex
from hexa

@@
 \begin{document}
-
-%\title{Universally emergent L=1 resonances}
-\title{Four-body L=1 systems from contact EFT}
-
-\author{Lorenzo Contessi}\email{lorenzo@contessi.net}
-\address{IRFU, CEA, Universit\'e Paris-Saclay, 91191 Gif-sur-Yvette, France}
-
-\author{Jaume Carbonel}
-\address{Universit\'e Paris-Saclay, CNRS/IN2P3, IJCLab, 91405 Orsay, France}
-
-\author{Johannes Kirscher}
-\address{Theoretical Physics Division, School of Physics and Astronomy,\\
-  The University of Manchester, Manchester, M13 9PL, UK}
-
-\author{Rimantas Lazauskas}
-\address{IPHC, IN2P3-CNRS/Universit\'e de Strasbourg BP 28, F-67037 Strasbourg Cedex 2, France}
-
-\author{Martin Sch{\"a}fer}
-\address{Nuclear Physics Institute of the Czech Academy of Sciences, 25069 \v{R}e\v{z}, Czech Republic}
-
-\date{\today}
-
-\begin{abstract} 
-Scattering resonances are ubiquitous in physics, and for the understanding of the behaviour of few-body quantum systems as important as bound states.
-Compared with the latter, their theoretical handling and their role in the interpretation of data is complicated through their unstable nature which is reflected in their belonging to the continuum spectrum.
-The smallest nuclear system comprised solely of resonances is 4-hydrogen with $L=1$ states about $3.5$~MeV above the triton-neutron
-threshold.
-
-In this article, we analyze the minimal contact theory which predicts
-such $P$-wave, four-body resonances. Furthermore, we establish numerically
-the emergence of this specific resonance pole for a wider class of systems
-whose two-body scale is significantly larger ($\to\infty$) than their interaction range.
-Specifically, we employ a contact effective field theory renormalized
-with nuclear observables (LO pionless effective field theory)
-and to unitary systems without a finite two-body scale (universal
-contact effective field theory). We find a negative-parity four-body
-resonance pole which is stable with respect to the short-distance structure
-of the regularized two- and three-body momentum-independent contact
-potentials with three independent numerical algorithms: a finite-volume
-Gaussian-stochastic-variational technique, the solution of the AGS on a
-discrete coordinate-space grid, and a one-channel, two-body,
-resonating-group reduction of the problem.
-Thereby we demonstrate that a zero-range potential
-provides a non-trivial pole structure for the four-body amplitude.
-\end{abstract}
-
-\maketitle
-
-\section{Introduction}
-
-Resonance phenomena occur ubiquitously in quantum and classical physics.
-Relative to stable bound states, their handling in many-particle hadronic, nuclear,
-and atomic physics is complicated. 
-A resonance results from a nonperturbative interplay of particle-particle interactions,
-fine-tuned potential shapes, and channel couplings that lead to multiple
-excitations and thresholds.
-Relative long life times and energies very close to production thresholds lead to
-clean, measurable signals, while in practise, a rapid decay and an energy far from
-threshold makes their identification with cross section data involved. 
-Theoretically, the structure of a Hamiltonian usually does not expose the existence of
-resonances without explicitly solving dynamical equations. In the latter course,
-numerical methods to extract complex energies are, in general, expensive and
-less accurate compared with those for bound states.
-%
-
-%
-In order to identify general features of an interaction which allow for the
-prediction of resonances, we focus on  the 4-hydrogen ($^4$H), the smallest nuclear system known to
-be characterized by a resonance.
-In this system, $J^\pi=0^-, 1^-, 2^-$ resonances are found experimentally approximately
-$5.2$~MeV, $3.5$~MeV, and $3.2$~MeV, respectively, above the triton-neutron threshold.
-Cross sections and scattering parameters have been studied extensively both experimentally
-~\cite{osti_4230875, Phillips:1980zz, Tilley:1992zz}~and theoretically~
-\cite{Ciesielski:1997vy,Ciesielski:1998sy,Ciesielski:1999pp,Viviani:1998gr,Fonseca:1999zz,Lazauskas:2004uq}.
-The position of the $^4$H, $J^\pi=1^-$ resonance pole was located in
-Refs.~\cite{Arai:2003ek,deDiego:2007rd,Lazauskas:2019cxj}~ at an energy
-$Re(E)=\{0.90 - 1.23\}$~MeV and width $\Gamma=\{3.5 - 5.8\}$~MeV.
-From data, a $R$-matrix analysis puts this pole at $Re(E)=3.50$~MeV and $\Gamma=6.73$~MeV~
-\cite{Tilley:1992zz}.
-Despite the quantitative discrepancy among theory and experiment, the sheer existence of the pole in different models is remarkable.
-%
-%
-%
-Why does
-such a pole emerge in the four-body amplitude but is absent, e.g., in the
-deuteron-neutron quartet channel or the three-neutron system? What are minimal
-conditions and characteristics of the employed models necessary for these features?
-These questions are crucial in the development of the nuclear effective field
-theory in order to make it useful for the description of heavier nuclei beyond
-the $S$ shell.
-Furthermore, fermi statistics which enforces higher relative angular
-momenta in ground-state wave functions of more than four nucleons, is equally
-relevant for hadronic, atomic, in general, all fermions amenable
-to a description with zero-range forces. Hence, an understanding how the structure
-of these forces leads to certain few-body resonance poles carries value far beyond the
-$^4$H system, namely: is a leading-order description of a system of particles, whose
-statistics demand mixed-orbital-symmetry states, with properly renormalized coupling
-strengths of zero-range, possibly spin-/flavour-dependent interactions possible?
-%In this study, we are interested in both these aspects on the framework of very minimalists nuclear forces: renormalizable contact effective field theories. 
-%
-%
-%
-%
-
-%
-Such renormalizable effective field theories (EFT) were instrumental in understanding
-the relation between nuclear physics and its underlying theory of quantum chromodynamics
-and for deriving universal features which nuclei share with atoms.
-All EFT's comprise of the most general Lagrangean whose terms are built with
-appropriately chosen degrees of freedom and meet certain internal and space-time symmetries.
-A hierarchy (power counting) amongst this infinity of operators and their weight within
-an iterative expansion of the $S$-matrix renders the theory {\it effective}, i.e., useful.
-In the two-body sector, the convergence of the expansion and the choice of the relevant
-degrees of freedom depends on the typical momentum exchanged between interaction partners;
-for different typical momenta, different EFT expansions are needed. 
-For instance, few-body nuclear systems are close to the unitary limit, where the two-body
-scattering length is much larger than any other scale, an
-expansion around an infinite (or large) scattering length with solely nuclear degrees of freedom
-yields the bulk structure of nuclei up to 4-helium~\cite{vanKolck:1999mw}.
-For momenta that allow for the creation of pions, this pion-less power counting (\eftnopi)
-fails. For these momenta, chiral EFTs couple the pion field to the nucleons and thereby
-introduce long-range forces at leading order, while \eftnopi~is of zero-range at
-leading order and thus easier to treat numerically and analytically.
-Whether this simplicity of a zero-range theory still does not lead to an exclusion
-of complex many-body phenomena, e.g., shallow quantum states and resonance poles is
-unknown and shall be studied in this article.
-
-What is known about \eftnopi, in particular, is its ability to predict the behavior
-of many-boson systems and nuclei up to four nucleons. 
-However, the leading order (LO) of the theory cannot account for the observed behavior of
-multi-fermionic systems. There, it erroneously predicts unbound nuclei above four
-particles, e.g.~$^7$Li and $^{16}$O~\cite{Schafer:2020ivj,Contessi:2017rww}.
-It was conjectured more generally, that zero-range theories cannot sustain 
-bound states of mixed symmetry.
-However, the bound character of a state might appear only at a higher orders of the EFT
-provided that the LO creates a pole of other kind, virtual or resonant, which the
-modification of the interaction at higher order transforms into a bound state. 
-If no such pole is present at LO in these systems -- of which $^4$H is the smallest --
-only a modification of the power counting
-will furnish the correct description of nuclear physics with contact EFTs.
-
-The creation of resonant $S$-wave poles at LO \eftnopi~was demonstrated in case of the
-hyper triton ($nn\Lambda$) in Ref.~\cite{Schafer:2020rba} (as a subthreshold resonance) but
-there is no record of such poles being created renormalization-scheme independently
-in systems with mixed symmetry ground states
-such as $^4$H with a zero-range theory. 
-It is the aim of this work to analyze this creation of a four-body $P$-wave resonance
-pole from an zero-range, spherically-symmetric regularized contact interaction with
-coupling strengths resembling nuclear systems close to unitarity and also systems which
-realize this limit with an infinite two-body scattering length, i.e., zero-energy bound
-state.
-
-In the following section, we introduce the Hamiltonian of the theory along with
-comments on its solution with a Gaussian-stochastic-variational method, the
-treatment of the scattering problem via the Alt, Grassberger, and Sandhas equations
-in coordinate space, and the reduction of $N$-body, two-fragment scattering onto a
-two-body problem.
-Following this, we present results for effective-range parameters and pole positions
-for the low-energy scattering of a neutron on $^3$H before generalizing this to a
-generic point particle impinging on a universal trimer.
-Finally, we relate the regulator independence of the results to the deployed minimal
-theory as a first-order approximation of nuclei and universal, unitary systems.
-
-\section{Contact EFT and numerical methods}
-
-\begin{table}
-    \centering
-    \begin{tabular}{|ccc|}
-    \hline
-    \multicolumn{3}{|c|}{Nuclear LECs}\\
-    \hline
-         $\Lambda$ [fm$^{-1}$] & $C_0$ [MeV] & $D_0$ [MeV] \\
-1   &	-44.4552	&	27.2312 \\
-2	&   -142.376	&	172.703 \\
-3	&   -295.959	&	559.013 \\
-4	&   -505.202	&	1397.56 \\
-6	&   -1090.66	&	6311.30 \\
-10	&   -2929.48	&	89436.2 \\
-    \hline
-    \end{tabular}
-    \quad
-\begin{tabular}{|ccc|}
-    \hline
-    \multicolumn{3}{|c|}{Universal LECs}\\
-    \hline        
-        $\Lambda$  & $C_0$  & $D_0$  \\
-1	&   -0.671	&	0.678 \\
-2	&   -2.684	&	7.749 \\
-4	&   -10.736	&	194.253 \\
-6	&   -24.156	&	4273.294 \\
-8	&   -42.944	&	122391.358 \\
-10	&   -67.100	&	4102409.239 \\
-    \hline
-\end{tabular}
-    \caption{LECs fitted for each cut-off. In the left tab are listed the LECs fitted to reproduce deuterium and $^3$He energy in MeV. On the right the ones that reproduce unitary systems of nuclei.}
-    \label{tab:LECs_unprojected}
-\end{table}
-
-The minimal theory for the
-
-The leading order (LO) of the contact EFT we are employing consists of a contact two-body and a contact three-body operators with two low energy constants (LECs) to be fitted on physical observables \cite{vanKolck:1999mw}.
-A Gaussian regulator and a cut-off $\Lambda$ are introduced to smear the potential such that the contact limit is restored for $\Lambda\rightarrow+\infty$:
-
-\begin{equation}
-    V(\textbf{r})=C_0 \sum_{i,j}^N e^{-\frac{r_{ij}^2\Lambda^2}{4}}
-\end{equation}
-
-\begin{equation}
-    W(\textbf{r})=D_0 \sum_{ijk}^N \left[
-    e^{-\frac{(r_{ij}^2+r_{ik}^2)\Lambda^2}{4}}+
-    e^{-\frac{(r_{ij}^2+r_{jk}^2)\Lambda^2}{4}}+
-    e^{-\frac{(r_{jk}^2+r_{ik}^2)\Lambda^2}{4}}\right].
-\end{equation}
-
-Once the interaction is regularized the LECs ($C_0$ and $D_0$) become cut-off dependent and must be fitted for any $\Lambda$ to reproduce the chosen set of fixed two- and three-body observables.
-Nonetheless, if the theory is renormalizable this is sufficient to stabilize (in the sense of converging to a finite value) any other few- and many-body observable in the \textit{large cut-off limit}.
-We employ two different two-body potentials in this study, a central one and one projected in S-wave only. 
-This division is necessary for the numerical methods we use but is relevant only for small cut-offs.
-In fact, in the limit, $\Lambda\rightarrow\infty$, the projected and unprojected potentials converge to the same contact interaction essentially representing only a different choice of the regulator.
-Nonetheless, for small cut-off we expect and experience discrepancies, this results especially in different sets of three-body LEC $D_0$ that fix the three-body energy.
-Moreover, for each projected and unprojected interaction we fit two sets of LECs.
-The first, the "nuclear" one, fixes a single two-body boundstate of $B_2=2.22$ MeV (both in singlet and triplet channels).
-In the second, the "universal" ones, the LECs are fitted to reproduce a large two-body scattering length ($a_0>10^5$).
-In both cases, the three-body is fitted to reproduce a single three-body boundstate $B_3=-8.482$ MeV, and we employ the same nucleon mass to $m=938.858$ MeV, and the same $\hbar c= 197.31613$.
-As an example, in tab. \ref{tab:LECs_unprojected}, we report the nuclear and universal LECs for the unprojected interaction.
-%
-
-%
-Since \eftnopi is best suited for the description of low energy observables we refer to the effective range expansion (ERE) scattering parameter. 
-It is essentially the expansion in low momentum of the phaseshift of a relative angular momentum $L$ two-body problem phaseshift $\delta$:
-
-\begin{equation}
-    k^{2L+1}cot(\delta)=-\frac{1}{a_L}+\frac{1}{2}r_L k^2 + ... \, .
-\end{equation}
-
-The same expansion can be used either in the two-body problem and in the four-body one assuming that $^4$H can be seen as a $n-^3$H pair.
-Resonances will therefore emerge as poles of the system T-matrix
-
-\begin{equation}
-T = \frac{1}{k^{2L+1}cot(\delta)-ik}    
-\end{equation}
-
-and can be extracted either by fitting phaseshifts to the ERE formula or directly through solving the Schr\"odinger equation for complex energies.
-
-\subsection*{Numerical methods}
-
-In this work, we utilize three different methods to solve the $n-^3$H shr\"oedinger equation.
-The Rimas Method, the Stochastic Variational Method, and the Resonating Group Method. 
-Coupled with these technologies we use also the complex rotation and the Analytic Continuation of the Coupling Constant (ACCC) to determine the position of resonant solution of the four-body problem (belonging to the continuum and hard to be extracted with the conventional methods) and the scattering lengths and volumes of the $n-^3H$ reaction.
-
-**wrong and to be changed** 
-SVM consists of the variational search of the ground state of the problem using an over-complete set of Gaussians, chosen stochastically for each Jacobi coordinate, to represent the system wave function.
-This few-body method was developed by Lee Suzuki [] in ... and refined during the years to provide a reliable and relatively cheap solver for ground-state system up to $\sim 6$ particles.
-A review of the method can be found in [] and a deeper insight is given by [].
-
-%
-%- Just give an idea and the references -
-%
-%
-% RGM - SVM - ACCC - ?
-%
-
-%
-%
-%
-%
-%
-%
-%
-%
-%
-%
-
-\section{Procedure and results}
-
-\begin{figure}
-\centering
-\includegraphics[width=0.95\textwidth]{./Graphs/a0a1} 
-\caption{$1^-$ resonant pole in $^4$H}
-\label{fig:a0a1}
-\end{figure}
-
-Our discussion begins with the analysis of low energy scattering parameters of the $n-^3$H system. 
-This system allows for several low-energy states with relative angular momentum $J=1$ between the fragments: $0^-$, $1^-$, and $2^-$; we focus exclusively on the natural parity state: $1^-$. 
-We also study the state $0^+$, with relative angular momentum L=$0$. 
-This state is Pauli excluded, therefore, we do not expect any resonant or bound state in this channel but we still consider it interesting to study the EFT behavior and as a benchmark among different methods.
-In figure \ref{fig:a0a1} we shown the scattering length and volume (relative to $0^+$ and $1^-$ states) calculated using SVM and RIMAS microscopical approaches.
-Can be noticed how, for large enough cutoffs, the two methods are compatible.
-This was expected since the two calculations use effectively two different regulators due to the presence of an S-wave projected and unprojected two-body potential. 
-The difference between the two is more noticeable in the $J^\pi=1^-$ channel as the effect of P-wave interactions is more evident.
-The two scattering parameters converge with the cut-off to a finite value. 
-This fact is nontrivial since the interparticle interaction converges to a contact potential for large cut-offs.
-In fact, $n$ and $^3H$ contain an identical fermion which suppresses any positive parity interaction.
-However, the contact nature of the potential allows only particles in relative S-wave to interact. 
-The finiteness of $a_0$ and $a_1$ should, therefore, be explained by the mediation of the distinguishable fermions and by the few-body effects.
-$a_0$ and $a_1$ converge, empirically, as $1/\lambda$. 
-In other words, since the interplay of S-wave interactions can result in a finite interaction in P-wave among few-body clusters, the scattering length/volume remains finite even only including the theory LO.
-As a consequence, their cut-off behavior is $\propto1/\Lambda$ as expected by LO observables.
-The sign and magnitude of the converged results ($a_0\simeq 3.1$ fm and $a_1\simeq-13(1)$) indicate the absence of boundstates, but the $a_1$ magnitude might indicate the presence of a shallow pole in the $1^-$ system.
-It is also interesting to notice that the effective range for $0^+$ and $1^-$ remains also finite ($r_0\simeq2$ fm and $r_1\simeq1$ fm respectively).
-This is also expected since, despite the nucleon-nucleon interaction is of contact nature, the size of the fragments remains finite, allowing for an inter-fragment long-range effect.
-%
-
-While arguably the best method to extract phaseshifts and resonance positions, the microscopic approach becomes more and more complicated and unfeasible when the number of particles is increased. 
-For this, we would like to tackle the same problem from a different perspective: using the RGM formalism.
-RGM intrinsically contains an approximation in the form of a simplified few-body wave function of one of the fragments.
-It is, however, easily extendable to larger systems.
-In our case, RGM transform a four-body problem into a simplified two-fragment one at the price of
-
-%
-%
-\begin{figure}
-\centering
-\includegraphics[width=0.95\textwidth]{./Graphs/E4H} 
-\caption{$1^-$ resonant pole in $^4$H}
-\label{fig:Resonance_pole}
-\end{figure}
-%
-
-%
-The second step in our calculation is the determination of the $J^\pi=1^-$ nuclear resonance position in the Energy complex plane. 
-This has been done using the ACCC method starting from "RIMAS" numerical method. 
-In figure \ref{fig:Resonance_pole}, the evolution of such pole can be follow to pass the threshold energy $B_{t}=8.484$ MeV ($Re(E)=0$ in the plot) to stabilize around $E_{n-t}=-8.7-i\,3.1$ for cutoffs greater than $6$ fm$^{-1}$.
-This represents a shallow and broad subthreshold resonance. 
-The presence of such a state and especially its stability (in this case expressed as a pole that does not run to infinite energy increasing the cut-off) is not trivial for the same reasons as one might not expect scattering length/volumes larger than zero.
-%
-Therefore, this proves that the theory is able to predict shallow states in systems with mixed symmetry. 
-However, the position of the LO EFT pole appears to not be compatible with the physical resonance in $^4H$: ???
-($E_{n-t}=8.17+i\,6.73$).
-%\cite{http://tunlweb.tunl.duke.edu/nucldata/ourpubs/04_1992.pdf}.
-where does this come from?
-???
-Nonetheless, the theory is only tested at LO where the relevant operators to describe such states are not been yet introduced.
-It is not in principle problematic that the LO pole is not consistent with the experimental data since including the subleading orders (NLO and N$^2$LO) can, even in a perturbative treatment of the expansion, relocate it in the correct position.
-However, in this process one should be careful that the insertion of the subleading operators does not shift unreasonably, neither too much nor in the wrong direction, any of the other observables (e.g.
-the $^4He$ energy or the $n-^2H$ phaseshifts).
-At the current knowledge of the authors, no studies have ever been done in this sense and the possibility of a consistent correction of a resonant pole in therms of powerconting hierarchy remains to be demonstrated.
-%
-
-\subsection*{Universality}
-
-%
-In the framework of universal systems, in which the two-body scattering length is divergent, the scattering volume of $n-^3H$ follows an identical pattern as before, but with a convergent value of $\sim4$ fm$^3$.
-This can be compared to the typical coordinate scale of the system, which, in this case, is uniquely identifiable with the three-body scale $R_3=(-2mE_3/\hbar^2)^{-1/2}\simeq 6$ fm. 
-We find that $(a_1)^{-1/3}/R_3 \simeq  1/4$, which is a small, but still natural ratio.
-
-** here I have some discrepancies (martin A11 is twice Rimas A11)
-\begin{figure}
-\centering
-\includegraphics[width=0.95\textwidth]{./Graphs/unitarityA} 
-\caption{Temporary: unitary scattering lengths / volume}
-\label{fig:Resonance_pole}
-\end{figure}
-**[martin pole and data for unitarity]**
-
-\section{conclusion}
-
-\bibliographystyle{ieeetr}
-%elsarticle-harv}
-\bibliography{bibi.bib}
 
@@
 we chose to express the wave function of the system with a two-cluster, single-channel ansatz
-without specific distortion:
+without specific distortion (\cf\eref{eq.app.rgmwfkt}, first term):
 
@@
 
-\cf\eref{eq.app.rgmwfkt}, first term. The parameter representation employed with the second equality in \eref{eq.app.rgmwfkt2}
+The parameter representation employed with the second equality in \eref{eq.app.rgmwfkt2}
 will yield a defining equation for the relative motion independent of the antisymmetrizer $\mathcal{A}$.
-Assuming an inert triton core allows solely for a variation of the relative wave function:
+Assuming an inert triton core ammounts to a variation of the relative wave function, only:
 
@@
  $\mathcal{A}_{31}=\mathbb{1}-\hat{P}_{14}$.
-We chose nucleons 1 and 4 to be the neutrons with identical spin orientation, and hence need to consider the permutation of
-those particles, only. All other permutations $\hat{P}_{ij}$ will yield zero matrix elements because of the orthogonality of
+We chose nucleons 1 and 4 to be the neutrons with identical spin orientation, and hence need to permutate only
+those particles. All other permutations $\hat{P}_{ij}$ will yield zero matrix elements because of the orthogonality of
 the internal states.
@@
 
-(iv)~performing the action of $\mathcal{A}_{31}$ on $\phi_3$ and $\delta(\ve{R}-\ve{R}\mprime)$;
+(iv)~acting with $\mathcal{A}_{31}$ on $\phi_3$ and $\delta(\ve{R}-\ve{R}\mprime)$;
 and finally, (v)~doing the Gaussian integrals for the triton-internal single-particle coordinates $\ve{r}_{1,2,3}$.
@@
 before substituting
-$$
-e^{-b\ve{R}\cdot\ve{R}'}=4\pi\sum_{LM}i^Lj_L(ib RR')Y^*_{LM}(\hat{\ve{R}})Y_{LM}(\hat{\ve{R}}')\;\;;\;\;
-\ve{R}\cdot\ve{R}'=-\sqrt{3}\coup{\ve{R}_p}{\ve{R}\mprime_{-p}}{00}=\frac{4\pi}{3}RR'\sum_p(-)^p\,Y_{1p}Y'_{1-p}
-$$
-and $\ve{r}_m=\sqrt{\frac{4\pi}{3}}rY_{1,m}(\hat{\ve{r}})$
+\begin{eqnarray}
+e^{-b\ve{R}\cdot\ve{R}'}=4\pi\sum_{LM}i^Lj_L(ib RR')Y^*_{LM}(\hat{\ve{R}})Y_{LM}(\hat{\ve{R}}')\qquad,\\
+\ve{R}\cdot\ve{R}'=-\sqrt{3}\coup{\ve{R}_p}{\ve{R}\mprime_{-p}}{00}=\frac{4\pi}{3}RR'\sum_p(-)^p\,Y_{1p}Y'_{1-p}\qquad,
+~\text{and}\qquad\ve{r}_m=\sqrt{\frac{4\pi}{3}}rY_{1,m}(\hat{\ve{r}})\qquad,\\
+\end{eqnarray}
 yields
@@
 \centering
-\includegraphics[width=0.95\textwidth]{./Graphs/rgm_potential} 
+\includegraphics[width=0.95\textwidth]{./Graphs/rgm_potential_nucl} 
 \caption{Two-fragment potential as a function of the distance between a
@@
 The non-local parts are evaluated at $R=R'$. The height of the potential's barrier shrinks continuously from
-the smallest cutoff (fat blue) to the largest (red), with intermediate values represented by green, dashed curves.}
+the smallest cutoff (red) and eventually vanishes at the largest (fat blue), with intermediate values represented by green, dashed curves.}
 \label{fig:rgm_potential}
 \end{figure}
-
-\begin{figure*}[th]
-\captionsetup{width=.4\linewidth,justification=raggedright}
-\begin{tabular}{cc}
-\begin{minipage}[t]{0.45\linewidth}
- \includegraphics[width=\textwidth]{./Graphs/rgm_potential_MinMax}
- \caption{Locus of the valley (red, dashed) and the barrier (blue, solid) of the effective resonating-group
- interaction (\figref{fig:rgm_potential}) as a function of the regulator parameter $\lambda$.}
-\label{fig:rgm_pot_minmax}
-\end{minipage}
-&
-\begin{minipage}[t]{0.45\linewidth}
- \includegraphics[width=\textwidth]{./Graphs/rgm_potential_DeltaMinMax}
-\caption{Regulator dependence of the difference between the first local maximum of the effective resonating-group potential
-(\figref{fig:rgm_potential}) and its first local minimum.}
-\label{fig:rgm_pot_valbardiff}
-\end{minipage}
-\end{tabular}
-\end{figure*}
+%
+%\begin{figure*}[th]
+%\captionsetup{width=.4\linewidth,justification=raggedright}
+%\begin{tabular}{cc}
+%\begin{minipage}[t]{0.45\linewidth}
+% \includegraphics[width=\textwidth]{./Graphs/rgm_potential_MinMax}
+% \caption{Locus of the valley (red, dashed) and the barrier (blue, solid) of the effective resonating-group
+% interaction (\figref{fig:rgm_potential}) as a function of the regulator parameter $\lambda$.}
+%\label{fig:rgm_pot_minmax}
+%\end{minipage}
+%&
+%\begin{minipage}[t]{0.45\linewidth}
+% \includegraphics[angle=90,width=\textwidth]{./Graphs/rgm_potential_DeltaMinMax}
+%\caption{Regulator dependence of the difference between the first local maximum of the effective resonating-group potential
+%(\figref{fig:rgm_potential}) and its first local minimum.}
+%\label{fig:rgm_pot_valbardiff}
+%\end{minipage}
+%\end{tabular}
+%\end{figure*}
 

### 2022-06-18 manuscript/Draft_0.4.tex
from hexa

%\documentclass[aps,onecolumn,preprintnumbers,amsmath,amssymb,nofootinbib,superscriptaddress,notitlepage]{revtex4-1}
%\documentclass[preprint,12pt]{elsarticle}
\documentclass[5p,times]{elsarticle}
%\documentclass[aps,nofootinbib,prl,showpacs,twocolumn,groupedaddress,superscriptaddress]{revtex4}

\usepackage{graphicx}
\usepackage{dashrule}
\usepackage{dcolumn}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{bbold}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{wasysym}
\usepackage{slashed}
\usepackage[dvipsnames]{xcolor}
\usepackage{soul}
\usepackage{rotating}
\usepackage{paracol}
\usepackage{nicefrac}
\usepackage{MnSymbol}

%\usepackage{subcaption}
%\newbox{\bigpicturebox}

\newcommand{\reales}{{\rm R}\hspace{-1ex}\rule{0.1mm}{1.5ex}\hspace{1ex}}
\def\tstrut{\vrule height2.5ex depth0pt width0pt} % used in tables
\def\jtstrut{\vrule height5ex depth0pt width0pt} % used in tables

\newcommand{\figref}[1]{fig.~(\ref{#1})}
\newcommand{\tabref}[1]{table~(\ref{#1})}
\newcommand{\ccite}[1]{ref.~\cite{#1}}

\newcommand{\eref}[1]{eq.~(\ref{#1})}
\newcommand{\eg}{\textit{e.g.}~}
\newcommand{\ie}{\textit{i.e.}~}
\newcommand{\viz}{\textit{viz.}~}
\newcommand{\cf}{\textit{cf.}~}
\newcommand{\eftnopi}{\mbox{EFT($\slashed{\pi}$) }}
\newcommand{\ve}[1]{\ensuremath{\boldsymbol{#1}}}
\newcommand{\rcm}{\ensuremath{\ve{R}_\text{\scriptsize{c.m.}}}}
\newcommand*{\mprime}{^{\prime}\mkern-1.2mu}
\newcommand*{\mdprime}{^{\prime\prime}\mkern-1.2mu}
\newcommand*{\mtprime}{^{\prime\prime\prime}\mkern-1.2mu}
\newcommand{\ddrei}[1]{\delta_{\tiny \lambda}^{(3)}\!\big(#1\big)}
\newcommand{\cc}{\ensuremath C(\lambda)}
\newcommand{\dd}{\ensuremath D(\lambda)}
\newcommand{\hbstwom}{\ensuremath \frac{\hbar^2}{2\mu}}
\newcommand{\twomhbs}{\ensuremath \frac{2\mu}{\hbar^2}}
\newcommand{\coup}[3]{\left[\,#1\,\otimes\,#2\,\right]^{#3}}
\newcommand{\threej}[6]{ \begin{pmatrix}
   #1 & #2 & #3 \\
   #4 & #5 & #6
  \end{pmatrix}}

\newcommand{\bra}[1] {\left\langle~#1~\right|}
\newcommand{\ket}[1] {\left|~#1~\right\rangle}
\newcommand{\bet}[1] {\left|#1\right|}
\newcommand{\overlap}[2] {\left\langle\,#1\,\left|\,#2\,\right.\right\rangle}
\newcommand{\me}[3] {\left\langle\,#1\,\left.\left|\,#2\,\right|\right.\,#3\,\right\rangle}
\newcommand{\mer}[3] {\left\langle\,#1\,\left|\left.\,#2\,\right|\,#3\,\right.\right\rangle_{\ve{R}}}
\newcommand{\redme}[3] {\left\langle\,#1\,\middle|\right|\,#2\,\left|\middle|\,#3\,\right\rangle}

\definecolor{green}{HTML}{2E8B57}
\interfootnotelinepenalty=10000 %% Completely prevent breaking of footnote

\usepackage{xcolor}
\colorlet{darkgreen}{green!50!black}
\colorlet{brightyellow}{yellow!75!red}
\colorlet{orange}{red!50!yellow} \colorlet{darkred}{red!80!black}
\colorlet{darkblue}{blue!50!black}

\usepackage{soul}
\newcommand{\remove}[1] {\textcolor{darkred}{\st{#1}}}
\newcommand{\comment}[2] {\textcolor{green}{[\textbf{comment - #1}: {#2}]}}
\newcommand{\remark}[2] {\textcolor{orange}{[\textbf{\textsf{remark - #1}}: {\textsf{#2}}]}}
\newcommand{\highlight}[1] {\textcolor{red}{{#1}}}
\newcommand{\repl}[2] {\textcolor{darkred}{\st{#1}}\textcolor{blue}{#2}}
\newcommand{\place}[1] {\textcolor{blue}{{#1}}}
\newcommand{\edit}[1] {\textcolor{red}{{#1}}}

\begin{document}

\title{Emergence of $^4$H $J^\pi=1^-$ resonance in contact theories}

\author{Lorenzo Contessi}%\email{lorenzo@contessi.net}
\address{Universit\'e Paris-Saclay, CNRS-IN2P3, IJCLab, 91405 Orsay, France}
\address{IRFU, CEA, Universit\'e Paris-Saclay, 91191 Gif-sur-Yvette, France}

\author{Martin Sch{\"a}fer}
\address{The Racah Institute of Physics, The Hebrew University, Jerusalem 9190401, Israel}

\author{Johannes Kirscher}
\address{Department of Physics, SRM University - AP, Amaravati 522502, Andhra Pradesh, India}

\author{Rimantas Lazauskas}
\address{IPHC, IN2P3-CNRS/Universit\'e de Strasbourg BP 28, F-67037 Strasbourg Cedex 2, France}

\author{Jaume Carbonel}
\address{Universit\'e Paris-Saclay, CNRS/IN2P3, IJCLab, 91405 Orsay, France}

\date{\today}

\begin{abstract}

Elastic neutron-triton scattering is considered at leading order in pionless effective field theory.
In the infinite-cutoff limit, we obtain the scattering length $a_0(\infty) = 3.06(1)$~fm
and the effective range $r_0(\infty) = 1.59(7)$~fm ($S$-wave). 
In the $P$-wave channel, we predict a scattering volume $a_1(\infty) = -9.8(1.6)$~fm$^3$
and a range equivalent $r_1(\infty) = 1.3(4)$~fm$^{-1}$ with the same zero-range theory. 
%
The results are extracted with three numerical techniques: a
Gaussian-stochastic-variational method, an integration of the configuration-space Faddeev-Yakubovsky 
equations, and a resonating-group reduction of the four-body problem to an effective two-body cluster theory. 
Renormalization-group dependence is assessed through variation of a cutoff regulator parametrized in a
range between $1\,\text{fm}^{-1}$ and $10\,\text{fm}^{-1}$.
%
Most remarkably, we find a cutoff-stable/RG-invariant resonance in the $^4$H $J^\pi=1^-$ system.
This $P$-wave resonance is thus a universal consequence of the unitary deuteron system
and an ensuing discretely scale invariant three-body system with a scale set by the triton binding energy.
%
This stabilization of a resonant state in a few-fermion system solely through pure contact interactions
has a significant consequences for the powercounting of the pionless theory.
Specifically, the existence of a resonance implies that the known inability of the theory's leading order
to bind larger nuclei like 16-oxygen can be cured in perturbation theory.
\end{abstract}

\maketitle

%================================================
\section{Introduction}
%================================================

Contact effective field theory (EFT) is not only practical in describing
bosonic~\cite{Bazak:2016wxm,Carlson:2017txq,Bazak:2018qnu,Bedaque:1998kg,Bedaque:1998km} 
and few-nucleon~\cite{Bedaque:1999ve,Barnea:2013uqa} systems, it represents a systematic
expansion of the underlying scales and their interactions~\cite{Hammer:2019poc,Barnea:2013uqa}, and
thereby provides a transparent framework to study the emergence of many-body phenomena from few-body properties.
However, the nuclear incarnation of such a theory, Pionless effective field theory (\eftnopi), apparently fails to predict
stable bound states for $P$-shell
nuclei\footnote{Fermi systems with more particles than accessible internal states}
at the leading order (LO)~\cite{Stetcu:2006ey,Contessi:2017rww,Dawkins:2019vcr,Schafer:2020ivj}. 
%
For instance, the lightest of such nuclei, $^6 {\rm Li}$, is 
found unstable with respect to breakup into $\rm ^4He$ in its ground state ($\alpha$)
and a deuteron ($d$) in the zero-range contact limit~\cite{Schafer:2020ivj}~of LO~\eftnopi.
Whether or not the theory finds the physical bound state at LO veiled as a virtual or resonant state which
reveals its physical character at higher orders is arguably the most imminent problem of the development of contact EFTs for
Fermi systems.
As perturbative higher-order insertions cannot create poles {\it ex novo}, the conceivable absence of such poles
within the convergence radius of LO~\eftnopi~would make the theory in its current version useless for the description
of larger nuclei.
The challenge cast in simple words: Does the LO~\eftnopi~support any type of non-zero poles at complex momenta below its
breakdown scale?

Historically, resonances were studied in (A$\le$4)-body bosonic systems close to the unitary limit\cite{Deltuva:2012ig,deltuva2020energies} confirming the existence of a tower of Efimov resonances. 
A recent study\cite{Habashi:2020qgw} proved the possibility of creating two-body $S$-shell resonances in the contact limit with negative effective range.%, naidon2017efimov}. 
In the \eftnopi at LO framework, a resonance have been also found in neutral hypernuclear system $\Lambda nn$ \cite{Schafer:2020rba} and $S$-wave virtual states have been confirmed as exited states of triton \cite{Rupak:2019} and hypertriton \cite{Schafer:2020rba}. 
Finally, a recent study of $^3n$ confirmed the absence of $P$-wave resonance or virtual state in this system\cite{Dietz:2021haj}. 
At the present knowledge of the authors, the calculations of $P$-shell systems stops at this level and no studies have been done for discrete invariant systems of equal mass.
The major goal of this work is to study resonances in $^4$H a system never addressed before in this framework and that can be understood starting from its universal behavior. 
The existence of an eventual $P$-shell resonance using \eftnopi at LO would open the possibility of finding the same structure also in heavier nuclei, with the chance of stabilizing many-nucleon systems by perturbative corrections.
%

%
Experimentally, $^4$H resonances are clearly seen in n-$^3$H elastic cross sections \cite{PhysRev.119.1981,SEAGRAVE1972250}, as well as in $\pi^-$ absorption experiments \cite{Sennhauser:1981tr,Gornov:1991fg}, or in transfer reactions \cite{Miljanic:1986zz,Sidorchuk:2003fwa}. 
However, extracted resonance parameters differ substantially, depending on the used protocol and on the underlying hypothesis in the data analysis. 
For instance, results of the same $\pi^-$+$^9$Be$\,\to\,$d+t+$^4$H experiment, performed by the same authors, yields for the lowest state ($E_R$=3.0$\pm$0.2~MeV, $\Gamma$=4.7$\pm$1~MeV) \cite{Gornov:1991fg}, ($E_R$=2.0$\pm$0.2~MeV, $\Gamma$=1.2$\pm$0.2~MeV) \cite{Gurov:2005sp}, and ($E_R$=1.6 $\pm$0.1 MeV, $\gamma^2$=0.4$\pm$0.1~MeV)\cite{Gurov2005p}, where $\gamma$ is the reduced width (see the original paper), depending whether one assumes the experimental signal to be created respectively by one, two, or three resonant states.
Independently, the $R$-matrix analysis of n-$^3$H cross section \cite{Tilley:1992zz} concluded about a superposition of several $P$-waves resonant states with quantum numbers $J^\pi$=$0^-$,$1^-$,$2^-$. 
With two non-degenerate $J^\pi$=$1^-$ states (denoted $1^-_I$ and $1^-_{II}$ ) corresponding to two different total spin contributions in the asymptotic channels\cite{Lazauskas:2004uq}. 
The lowest state parameters found in this case ($E_R$=3.2 MeV, $\Gamma$=5.4 MeV) are hardly compatible with the previous many-state analysis. 
The discrepancies among different experimental approaches further
increase when including the transfer reaction experiments.
%

From a numerical point of view, computing the $S$-matrix pole of a resonance is not an easy task. 
Microscopic ab initio calculations for nuclear few-body systems are therefore not abundant and up to now have been performed for a limited amount of particles ($A<6$) \cite{Li:2019pmg,Lazauskas:2019cxj}. 
This limit is often circumvented by changing the calculation
degrees of freedom and treating the many-body systems as a few-body problem between clusters as done in Ref.~\cite{Arai:2003ek,deDiego:2007rd} introducing approximations in the solution \cite{doweneedthis}.
Resonances in $^4$H have been studied in the past, for example, in Ref.~\cite{deDiego:2007rd} using an effective two-body n-$^3$H potential adjusted to reproduce the $p$-$^3$He experimental phase shifts. 
Here, the resonance energy has been calculated either directly computing the $S$-matrix pole or by performing a $R$-matrix analysis of the phase shifts, showing a sensible difference among the two methods (the $1^-_I$ resonance is located at energy $E_r=1.2$, $\Gamma=3.5$ MeV, and $E_r=3.6$, $\Gamma=5.3$ MeV respectively).
%
% I dont know why this was removed, but it is the main point of the above paragraph
This result further enhances the difference between the position of the S-matrix pole and the resonance position extracted from the cross section, making difficult any kind of comparison between different calculations and experiments.
%
Other calculations have been done in Refs.~\cite{Arai:2003ek,Horiuchi:2013iw,Lazauskas:2019cxj,Li:2021ado} using the resonating group method (RGM) with complex scaling, Spin-dipole strength functions, Faddeev-Yakubowski equations (FYE) in configuration space, and No-core Gamov Shell Model. The results differs from method to method varying in a range $E_R=\{0.9-3.6\}$ MeV and $\Gamma=\{1.0-5.3\}$ MeV.
This variation appears to be a consequence of the different numerical techniques used more than on the interaction employed. In fact, studying the position of the resonance with different realistic interactions but the same theoretical scheme \cite{Lazauskas:2019cxj,Li:2021ado} leads to comparable results.

%
%

In this letter, we study the emergence of a 3+1 $J^{\pi}=1^-$ resonance in $^4$H using LO \eftnopi, demonstrating the possibility of creating n$^3$H $P$-wave states using a purely $S$-wave contact interaction. 
In the region of resonance projectile neutron momentum is $\sim 0.5~m_\pi$, binding momenta of nucleons within $^3$H target are $\sim 0.4~m_\pi$ (for a combined distance from the complete disintegration threshold of $0.8~m_\pi$): thus $^4$H resonant states are at the limit of convergence of \eftnopi, nevertheless still observable in a LO calculation. The absence of any spin-orbit or tensor term in the LO interaction causes degeneracy between $J^{\pi}=0,^-,1^-_I,1^-_{II},2^-$ states which would be splitted including higher orders. 
As $^4$H can still be treated as both a four-body and two-cluster (triton-neutron) system, we choose to employ both the methodologies starting from the same nuclear Hamiltonian.

%================================================
\section{Theory and numerical methods}
%================================================

The theory used in this work is the \eftnopi\cite{vanKolck:1999mw} truncated at LO. The lowest order consists of contact two-body and a contact three-body interactions with corresponding low energy constants (LECs) fitted to reproduce physical observables. To further simplify the theory we truncate it around the SU(4) symmetry \cite{Konig:2016utl}. %the theory is perturbative around su(4) symmetry, so we do not assume but we truncate it
Therefore, $NN$ spin-singlet and spin-triplet interactions are identical and only one contact term appears in the two-body sector. This adds further uncertainty to the theory of order $(a_0m_{\pi})^{-1}\sim30\%$ on the top of the usual \eftnopi LO truncation error. The contact interactions are regularized by an introduction of a Gaussian regulator and a momentum cut-off $\Lambda$. This yields two- and three-body potential 
%
\begin{equation}
    V(\textbf{r})=C_0 \sum_{i,j}^N e^{-\frac{r_{ij}^2\Lambda^2}{4}},
\end{equation}
%
\begin{equation}
    W(\textbf{r})=D_0 \sum_{ijk}^N \left[
    e^{-\frac{(r_{ij}^2+r_{ik}^2)\Lambda^2}{4}}+
    e^{-\frac{(r_{ij}^2+r_{jk}^2)\Lambda^2}{4}}+
    e^{-\frac{(r_{jk}^2+r_{ik}^2)\Lambda^2}{4}}\right],
\end{equation}
%
where the cut-off dependent LECs ($C_0$ and $D_0$) are fitted on two-body observables and triton binding energy ($B_3=8.48$~MeV). 
In order to assess the uncertainty introduced by the adoption of SU(4) symmetry, we use two different parametrizations for the two-body LEC $C_0$: one at unitarity (with $|a_0|>10^5$~fm and referred to as ``unitary'') and one fitting the deuteron binding energy $B_2=2.22$~MeV (referred as ``nuclear''). We assume a degenerate nucleon mass $m=938.858$ MeV.

To extract the effective range parameters and resonance energy we employ and compare results of three different methods. We use two ab initio techniques (four-body calculations): the direct solution of the Faddeev-Yakubovsky equations (FYE) in configuration space \cite{Lazauskas:2004hq, Lazauskas:2019hil} and the stochastic variational methods (SVM)\cite{Suzuki:1998bn}; 
and a potential folding technique that reduces the problem into effective two-body problem, represented by neutron impinging on a solid triton core.

Employing the above interaction we extract the triton-neutron scattering parameters ($a_L$ and $r_L$) for $L=0$ and $L=1$ trough the effective range expansion (ERE) expanded around the triton-neutron threshold:
%
\begin{equation}
    k^{2L+1}\text{cot}(\delta_L)=-\frac{1}{a_L}+\frac{1}{2}r_L k^2 + ... \, ,
    \label{eq.app.ere}
\end{equation}
%
where $\delta_L$ is the triton-neutron phase-shift at angular momentum $L$ and $k$ is the center of mass momentum of the fragments. 
Resonances will, therefore, emerge as poles of the system's $T$-matrix
%
\begin{equation}
T =\frac{4\pi}{m}\frac{1}{\text{cot}(\delta)-i} =
\frac{4\pi}{m}\frac{k^{2L+1}}{\frac{1}{a_L}+...+\frac{1}{2}r_L k^2
-ik^{2L+1}} \label{eq:Tmatrix}
\end{equation}
%
and can be extracted either by fitting phase shifts to the ERE formula or directly through solving the Schr\"odinger equation for complex energies.
%
From an theoretical point of view, extracting the resonance energy with the two methods is not equivalent. 
Solving the Schr\"odinger equation for complex energies is affected by the \eftnopi LO truncation error ($\Gamma_{\eftnopi}\approx k_{res}/m_\pi\sim80\%$), while extracting the resonance position using the ERE of the triton-neutron phaseshift and using RGM formalism (see below) is equivalent to the halo-EFT expanded around t-n treshold.
In the latter case, a new scale, the breaking momentum of $^3$H, is introduced at momentum $K_{d-n}\simeq94$ MeV. 
Since the scattering parameters are extracted using \eftnopi at LO we expect the two methods to agree inside the truncation error $\Gamma_{Halo}\approx k^*_{res}/K_{d-n}\simeq70\%$ using only the scattiring volume and $\Gamma_{Halo}^2$ %should be square, but if someone recheck is better
if the effective range $r_1$ is also included in the ERE.

\vspace{2mm}

%================================================
\subsection{Faddeev-Yakubovsky equation formalism}
%================================================

This formalism, as well as our employed numerical techniques, have been described in detail in Refs.~\cite{Lazauskas:2004hq,Lazauskas:2019hil}.
Here we will just stress that, in order to determine n-$^3$H scattering lengths (volumes), we solve the differential FYE equations by requiring the systems wave function to satisfy boundary condition in the far asymptote for retrieving neutron, defined by:
%
\begin{equation}
\begin{split}
\Psi(X_{^3{\rm H}},\vec{y}_{n-^3{\rm H}})=&\lim_{k\rightarrow0}\psi_t(X_{^3{\rm H}})\big([j_L(k|y_{n-^3{\rm H}}|)/k^{L}]\\
&+a_L(k) [n_L(k|y_{n-^3{\rm H}}|)k^{L+1}]\big)Y_L(\hat{y}_{n-^3{\rm H}});  \label{eq:FYe_a}
\end{split}
\end{equation}
%
here $j_L(z)$ and $n_L(z)$ are spherical Bessel functions of the first and second kind respectively. 
$\psi_t(X_{^3{\rm H}})$ is the wave function of the $^3$H ground state, which is found before undertaking n-$^3$H scattering calculations. 
In the particular case of determining the scattering lengths (volumes) $a_L$, calculations are performed for vanishing momenta $k$.
Note that, in the limit $k\rightarrow0$, the expressions in the brackets are finite functions depending on a distance $|y_{n-^3{\rm H}}|$.

To determine positions of the resonant states we solve FYE by imposing slightly different boundary condition for neutron asymptote:
\begin{equation}
\begin{split}
\Psi(X_{^3{\rm H}},\vec{y}_{n-^3{\rm H}})=&\psi_t(X_{^3{\rm H}}) \big(h_L^+(k_{r}|y_{n-^3{\rm H}}|)\\
&+F_L(k_r)h_L^-(k_{r}|y_{n-^3{\rm H}}|)\big) Y_L(\hat{y}_{n-^3{\rm H}});  \label{eq:FYe_res}
\end{split}
\end{equation}
here $h_L^-(z)$ and $h_L^+(z)$ are Spherical Bessel functions of the third kind. Complex momentum plane $k_r$ is scanned to find positions where the function $F_L(k_r)$ vanishes and thus wave function $\Psi(X_{^3{\rm H}},Y_{n-^3{\rm H}})$ represents purely outgoing n-$^3$H waves.

%================================================
\subsection{Harmonic oscillator trap}
%================================================
The second microscopic approach involves an introduction of the Harmonic oscillator (HO) trapping potential
\begin{equation}
    V_{\rm HO}(\textbf{r}) = \frac{m}{2A} \omega^2 \sum_{i<j} (\textbf{r}_i - \textbf{r}_j)^2
\end{equation}
with oscillator frequency $\omega$ into $A=4$-body $^4$H system.

Assuming that the range of an interaction is much smaller than the typical HO trap range $R << b_{\rm HO} =\sqrt{2/(m \omega)}$ one can match asymptotic $n ^3$H part of a trapped $^4$H wavefunction to the trapped solution of effective $n ^3$H two-body system with no nuclear interaction considered. The $n ^3$H phasehifts $\delta_L$ at relative momentum $k$ are then extracted using generalized Bush formula for an arbitrary orbital momentum $L$ \cite{Suzuki:2009}

\begin{equation}
    (-)^{L+1} \left(\sqrt{4\mu \omega}\right)^{2L+1} \frac{\Gamma\left(3/4 + L/2 - \epsilon^n_\omega/2\omega\right)}{\Gamma\left(1/4 - L/2 - \epsilon^n_\omega/2\omega\right)} = k^{2L+1}~{\rm cot}\left(\delta_L \right),
\end{equation}
where $ k=\sqrt{2\mu \epsilon^n_\omega}$, $\Gamma(x)$ is a Gamma function, $\mu \simeq 3/4 m$ denotes $n ^3$H reduce mass, and $\epsilon^n_\omega = E_\omega (^4{\rm H})-E_\omega (^3{\rm H})$ is an energy of the $n$-th $^4$H excited state in a trap with respect to the $n ^3$H threshold. Here, bound state energies $E_\omega (^3{\rm H})$, $E_\omega (^4{\rm H})$ are calculated using Stochastic Variational Method \cite{Suzuki:1998bn}. Both $S$-wave ($L=0$) and $P$-wave ($L=1$) $n ^3$H phaseshifts are extracted applying HO trap lengths $40~{\rm fm} \leq b_{\rm HO} \leq 60$~fm.

%================================================
\subsection{Resonating Group Method}
%================================================
Finally, the RGM technique was used to fold the two- and three-body interactions between the three particles in $^3$H and
the neutron in an effective n-$^3$H potential. This is done assuming that the $^3$H wave-function can be approximated as a sum of single Gaussians and that the scattering process happens at low energy such that no excitation can be created.
%
The input of this procedure is the $^3$H wave function, which has been extracted as the square root of the three-body single-particle density distribution calculated using the SVM. 
A linear combination of 5 Gaussians was used to parametrize the $^3$H wavefunction (the number of Gaussians was increased up to 8 without appreciable changes in the results). 
The requirement of having as input the wave function of the cluster makes the method dependent (and the result sensible) on a microscopic calculation. 
However, the possibility of transforming a four-fermion scattering problem into a simpler two-body problem is considered advantageous.
%
On one hand, the RGM potential loses some of the microscopic symmetries of the initial Hamiltonian, namely, it is non-local, energy-dependent, and non-Hermitian. 
On the other, the folded two-body scattering problem can be solved numerically relatively easily with the finite difference method. The method is also scalable and can be applied to larger systems in which microscopic scattering calculations are prohibitive.
%
Moreover, and beyond the simplification of the many-body scattering calculation, RGM also allows for simple visualization
of the effective cluster-particle interaction (after a particular regulator and cut-off configuration is chosen).
%
%\highlight{The details of the folding procedure and the folded interaction can be found in the attached document.}

%================================================
\section{Results and discussion}
%================================================

\begin{figure*}
\centering
  \centering
  \includegraphics[width=\linewidth]{Graphs/ere.pdf}
  \caption{Left panel : $S$-wave scattering length $a_0$ and effective range $r_0$ calculated using microscopic techniques, SVM with Bush Formula and solving the Faddeev-Yakubovsky equation (red), and n$^3$H folding using RGM (blue) for the "nuclear" case. Right panel : the same as in the left panel but for $P$-wave scattering parameters - scattering volume $a_1$ and $P$-wave effective range $r_1$. For each scattering parameter the corresponding dashed line represents an extrapolation to the contact limit ($\Lambda \rightarrow \infty$) using the function in eq.~\ref{extrapolation}. The extrapolated values together with extrapolation uncertainties are shown by the shaded bands.}
  \label{fig:ERE_Parameters}
\end{figure*}

We examine the scattering parameters of the n$^3$H system calculated with the microscopic methods (SVM with Bush Formula and solving the Faddeev-Yakubovsky equation). 
For scattering lengths $a_0$ and volumes $a_1$ we find relative agreement between two microscopic methods of order $\simeq 0.1-1 \%$ for $a_0$ and $\simeq 1-10\%$ for $a_1$ between the results. 
The effective ranges in $S$-wave ($r_0$) and $P$-wave ($r_1$) were extracted only via Bush formula and their numerical errors are not larger than $0.1$~fm and $0.1$~fm$^{-1}$, respectively.

The calculated $a_0,~r_0,~a_1$,~and~$r_1$ values using ab initio methods are shown as a function of increasing momentum cut-off $\Lambda$ in fig.~\ref{fig:ERE_Parameters}. 
As expected for \eftnopi LO observables, all scattering parameters converge as $1/\Lambda$. For $\Lambda \geq 4~{\rm fm^{-1}}$ we fit corresponding values using the function
\begin{equation}
    O(\Lambda) = O(\infty) +\frac{a}{\Lambda}
    \label{extrapolation}
\end{equation}
thus extrapolating calculated scattering parameters to the contact limit ($\Lambda \rightarrow \infty$). 
The resulting values extracted within \eftnopi at LO using the ``nuclear'' parametrization are: $a_0(\infty) = 3.06(1)$~fm, $r_0(\infty) = 1.59(7)$~fm for $S$-wave and $a_1(\infty) = -9.8(1.6)$~fm$^3$, $r_1(\infty) = 1.3(4)$~fm$^{-1}$ for $P$-wave, with extrapolation errors given in parentheses.
For the ``unitary'' $NN$ case we obtain $a_0(\infty) = 2.27(1)$~fm, $r_0(\infty) = 0.47(3)$~fm for $S$-wave n$^3$H scattering and $a_1(\infty) = -5.1(1)$~fm$^3$, $r_1(\infty) = 1.8(1)$~fm$^{-1}$ for $P$-wave n$^3$H scattering. 
%
In line with the sign convention adopted in eq. \ref{eq.app.ere}, the positive $a_0$ values suggest repulsive $S$-wave interaction, indicating dominance of Pauli principle between neutrons. 
This is in agreement with the lacking of bound state solutions in the $L=0^+$ n$^3$H channel for any $\Lambda$ considered. On the other hand, negative $a_1$s for all $\Lambda$ reveal attraction in $P$-wave n$^3$-H interaction. Approaching small-$\Lambda$ region, $|a_1|$ magnitude increases and the attraction becomes stronger, eventually resulting in the appearance of one $L=1^-$ bound state below $\Lambda\simeq$0.75 fm$^{-1}$. 
It is interesting to point out that, despite $S$-wave contact nature of the LO \eftnopi theory, the n$^3$H scattering has non-zero scattering volume and range components even in the $\Lambda \rightarrow \infty$ limit.
%
Comparing the ``unitary'' with the "nuclear" cases, both repulsion in $S$-wave and attraction in $P$-wave are preserved, however, for the former, the $a_0$ and $a_1$ are smaller in magnitude, which suggests in general weaker n$ ^3$H interaction in the "unitary" case.
%
On a universal scale the scattering parameters can be expressed in
natural units of the three-body scale $R_3=1/\sqrt{-2mE_3/\hbar^2}\simeq 6$~fm: the only scale present in the system. 
In this case, the scattering parameters are reasonably natural and read $|a_0(\infty)|\simeq0.4\,R_3$, $|r_0(\infty)| \simeq 0.1\,R_3$, $|a_1(\infty)|^{1/3} \simeq 0.3\,R_3$, and $|r_1(\infty)|^{-1} \simeq 0.1\,R_3$. %** check the numbers, might be outdated **
%

%
A comparison with the experimental data and the other theoretical models can only be done in $S$-wave (no data are available for scattering volumes and ranges). However, the $a_0$ calculated with ab initio methods as well as the RGM result appears to be compatible in sign and magnitude with the realistic calculations and experimental results available (inside \eftnopi truncation error), for both the ``nuclear'' and ``unitary'' parametrization used. 
As reference for theory and experiment we use the average scattering parameters $a_0^c=\sqrt{0.25(3a_{(S=1)}^2+1a_{(S=0)}^2)}$:   $a_0^{theo}=3.71$ fm\cite{Lazauskas:2019hil} and $a_0^{exp}=2.9\,-\,4.3$ fm\cite{Tilley:1992zz}, 
which are in good agreement with \eftnopi prediction considering the LO truncation uncertainty. 
%

%
Using the RGM method, the scattering parameters found are
$a_0(\infty) = 5.71$~fm, $r_0(\infty) \simeq 0.$~fm, $a_1(\infty) = -10.49$~fm$^3$, and $r_1(\infty) = 4.33$~fm$^{-1}$ for the ``nuclear'' parametrization; and
$a_0(\infty) = 3.3$~fm, $r_0(\infty) \simeq 1.8$~fm, $a_1(\infty) = -2.5$~fm$^3$, and $r_1(\infty) = 10.1$~fm$^{-1}$ fo the ``unitary'' case. 
These results are relatively distant from the ab initio calculation, however, it is hard to estimate the error introduced by the approximations done in the method and how they correlate with the expansion parameter of the theory.
Moreover, the RGM results appear to be highly sensitive to the $^3$H wave function used in the calculation, introducing a further dependence of the results from the input choice.
The result of RGM appear also to be natural and convergent (see Fig. \ref{fig:ERE_Parameters}) in the large cut-off limit.
%maybe we can add few more comments on this, but nothing comes in my mind.

%

%
\begin{figure*}
\centering
\includegraphics[width=.39\textwidth]{./Graphs/rgm_potential_unit}
\hfill
\includegraphics[width=.60\textwidth]{./Graphs/NonLocPot10_nuc}
\caption{\edit{change the capital R on left pannel and make sure it is the nuclear case}Left panel: Local part of the effective $P$-wave n$^3$H interaction $V(r,r')\delta(r'-r)$ as a function of the distance between the neutron and the center of mass of the triton. The interaction is extracted using the RGM at the n$^3$H zero energy and evaluated for different cut-offs from 1.5 (red line) to 10~fm$^{-1}$ (blue line); intermediate cut-offs are shown as green dashed lines. Right panel: Same as in the left panel but full non-local $V(r,r')$ interaction calculated for cutoff $\Lambda=10$~fm$^{-1}$.}\label{Fig:Potential}
\end{figure*}

%

%
\vspace{2mm}
%
Although the effective n$^3$H interaction is not observable, we use the RGM to extract its $P$-wave
component to acquire a deeper insight into interplay between repulsive and attractive parts and their evolution with $\Lambda$. In fig.~\ref{Fig:Potential}, we visualise such interaction for the "nuclear" case and zero-energy scattering. On the left panel, the local part of the coordinate space interaction ($r=r'$) is shown as a function of the distance between the neutron and the center of mass of the triton. 
A positive energy pocket at distance $r\simeq0.5$~fm can be noticed for small cut-offs, however, it vanishes approaching the contact limit ($\Lambda\to\infty$). On the right panel, the full coordinate interaction $V_{n-t}(r,r')$ is plotted for $\Lambda=10$~fm$^{-1}$ and zero energy. 
The non-symmetry of the interaction is a consequence of the folding technique. 
Here, the repulsive part of the interaction (red) clearly dominates and it can be traced as a combination between the repulsion induced by three-body forces, two-body exchange interaction, and centrifugal barrier. 
One can notice a weak attraction pocket ($min(V_{n-t})\approx$-0.35 MeV; blue) present far from the diagonal. 
The minimum of this pocket is too small to support a bound state, but it might be the reason for the appearance of a broad resonance state. This pocket is retained even for larger cut-offs.

\begin{figure*}
\centering
  \includegraphics[width=.98\linewidth]{Graphs/resonance.pdf}
  \caption{ Left panel : Complex energy plane with calculated $^4$H $1^-$ resonance positions (red crosses) for multiple momentum cutoff $\Lambda$. 
  The black triangles represent the position of the $1^-$ resonance extracted in Ref~\cite{Lazauskas:2019cxj}
  Right panel: The absolute value, real, and imaginary part of the complex resonance momentum $k^{res}_{n ^3{\rm H}}$ as a function of increasing $\Lambda$. The momentum is related to resonance energies via eqs.~\ref{mmnt}~and~\ref{kreim}. The resonance pole was extracted directly solving the four-nucleon problem trough the Faddeev-Yakubovsky equations.}
  \label{fig:Pole_PositionN}
\end{figure*}

%
So far our calculations revealed non-vanishing $P$-wave attraction in n$^3$H scattering in the contact limit, suggested by the negative $a_1(\infty)$, and the existence of attractive pocket in the effective n$^3$H $P$-wave RGM potential which persists even at highest considered cut-off $\Lambda=10$~fm$^{-1}$. Both of these results lead us, yet still not quite firmly, to an existence of a broad $^4$H resonance stabilizing with increasing momentum cut-off. Consequently, the final step in our calculation is to search directly for a position of the $J^\pi=1^-$ nuclear resonance looking for a pole of a 4-body $S$-matrix. This has been done by solving the Faddeev-Yakubovsky equations by imposing divergent boundary conditions provided by outgoing n$^3$H wave behavior.

In the left panel of fig.~\ref{fig:Pole_PositionN}, the evolution of such pole using the ``nuclear'' interaction is shown in the complex energy plane. It can be followed to pass the n$^3$H threshold energy $B_{t}=8.484$~MeV (denoted by dashed vertical line) finally stabilizing around $E^{res}=-8.7-i\,3.1$ for cutoffs greater than $6$~fm$^{-1}$. The passage of the resonance position from the fourth quadrant (${\rm Re}(E)>0$; ${\rm Im}(E)<0$) into the subthreshold third quadrant (${\rm Re}(E)<0$; ${\rm Im}(E)<0$) makes difficult to clearly visualise the convergence of the the resonance position with increasing $\Lambda$. 
Therefore, we transform calculated resonance energies into n-$^3$H complex momenta $k^{res}_{n ^3{\rm H}}$  
\begin{equation}
    k^{res}_{n ^3{\rm H}} = \sqrt{2 \mu E^{res}_{n ^3{\rm H}}},~~~~E^{res}_{n ^3{\rm H}}= E^{res} + B_{t},
    \label{mmnt}
\end{equation}
where $\mu \approx 3/4 m$ is the reduce mass of the two-body n-$^3$H system. The real and imaginary part of the complex momentum then can be evaluated as  
\begin{equation}
    \begin{split}
        {\rm Re}(k^{res}_{n ^3{\rm H}}) &= \sqrt{\frac{2\mu \left(|E^{res}_{n ^3{\rm H}}|+{\rm Re}(E^{res}_{n ^3{\rm H}})\right)}{2}},\\
        {\rm Im}(k^{res}_{n ^3{\rm H}}) &=  {\rm sgn}\left({\rm Im}(E^{res}_{n ^3{\rm H}})\right)\sqrt{\frac{2\mu \left(|E^{res}_{n ^3{\rm H}}|-{\rm Re}(E^{res}_{n ^3{\rm H}})\right)}{2}}.\\
    \end{split}
    \label{kreim}
\end{equation}

The ${\rm Re}(k^{res}_{n ^3{\rm H}})$, ${\rm Im}(k^{res}_{n ^3{\rm H}})$, and $|k^{res}_{n ^3{\rm H}}|$ momenta are plotted as a function of $\Lambda$ in the right panel of fig.~\ref{fig:Pole_PositionN}.  
For cut-off values larger than the breakup scale of the theory $m_\pi$ the resonance momentum starts to stabilize and its absolute value $|k^{res}_{n ^3{\rm H}}|$ does not exceed $0.35~{\rm fm}^{-1}\simeq 0.5 m_\pi$, remaining well inside the convergence radius of the theory (I.e., we do not expect subleading contributions to be able to remove this state from the theory).
%

%
We notice that the resonance position can also be found as pole of the n-$^3$H T-matrix in eq. \ref{eq:Tmatrix} parametrized by the scattering parameters calculated using \eftnopi. 
Truncating the ERE at the scattering volume we expect a deviation from the \eftnopi resonant momentum of $\Gamma_{halo}$: the expansion parameter of the n-$^3$H halo EFT at the resonant energy.
Doing this exercise we find a resonant momentum of $k^{res}_{halo})\simeq80+46\,i$ MeV, which is compatible, in the truncation error of the halo EFT, with the momentum of the \eftnopi pole ($k^{res}_{n ^3{\rm H}}\simeq46+49\,i$MeV).
Confirming that the pole is also inside the convergence value and can be treated in halo EFT.  
%

%
Comparing our $^4$H resonance result with experimental data and previous calculations, the major difference is that our pole goes to the subthreshold region in the $\Lambda\rightarrow\infty$ limit, namely, the resonance energy is lower than the n$^3{\rm H}$ threshold energy (notice that this kind of states are different than boundstates and remain non normalizable).
Theoretically, this is not an issue since the pole existence in subthreshold region does not break causality and it can be moved in the standard resonant region by a continuous transformation of the interaction (e.g. reversing the renormalization group transformation) and by the inclusion of \eftnopi subleading orders. 
% I dont like this statement bc the LO is compatible with a normal resonance and we expect this pole to go in the correct physical position at a certain point in the pionless expansion
%However, such a subthreshold resonance has only small impact on the physical observables and thus its signature would be almost impossible to be detected in an experiment.
%

%
Due to the difficulty of comparing different experimental set-up and theoretical calculations, it is hard to state to which extent our $^4$H resonance calculation is in agreement with the others in quantitative terms. 
%
To stress this point, one can notice that the $S$-matrix pole energy is, in general, lower than the one extracted with $R$-matrix analysis.
An illustrative example is provided by the  transfer reactions $^2$H(t,p)$^4$H and $^3$H(t,d)$^4$H \cite{Sidorchuk:2004ntw}. 
The $R$-matrix analysis of the results obtains for the lowest $^4$H state $E_R$=3.05$\pm$0.19 MeV and $\Gamma$=4.18$\pm$1.02 MeV while the corresponding $S$-matrix pole, extracted by the same authors, led to $E_R$ =1.99$\pm$0.37 MeV and $\Gamma_R$=2.85$\pm$0.3 MeV. 
Therefore, a fair comparison can only be done with other $S$-matrix pole predicted with realistic interactions. 
%
The study done in refs~\cite{Lazauskas:2019hil,Arai:2003ek, deDiego:2007rd} found a pole corresponding to ${\rm Re}(E_r)=(0.9\,-\,1.23)$~MeV and $\Gamma=(3.5\,-\,5.8)$~MeV.
\eftnopi at LO predicts a slightly less energetic but much narrower resonance ($E_r=-0.22$~MeV and $\Gamma=1.6$~MeV). 
The maximum relative distance between the poles momentum is $\sim 80\%$ of the total energy, although a large difference, it is in line with the expected uncertainty of the powercounting truncation.
%

%
The same calculations have been repeated using the ``unitary'' $NN$ interaction. In this case, Faddeev-Yakubovsky calculations find a wider resonance than in the nuclear case at energy $E_r=-8.156$~MeV and $\Gamma=2.4$~MeV (equivalent to absolute momentum $k_{n-t}=0.58\,m_\pi$). 
Despite this pole being relatively close to the one previously calculated (40\% of relative error: in line with the SU(4) assumption expected uncertainty), it is extremely hard to be tracked and has been studied only for cut-offs compatible with $m_\pi$: $\Lambda=0.75$ and $2$ fm$^{-1}$, and was not possible to check its value in the contact limit.

%================================================
\section{Conclusions}
%================================================
%
In this work, we observe the appearance of a stable $J^{\pi}=1^-$resonance in $^4$H using the pionless effective field theory (\eftnopi) truncated at leading order. The calculation is done using microscopic ab initio techniques as well as employing a folded interaction using the resonating group method (RGM).
%
Although other works have already established the possibility of creating shallow resonances using \eftnopi in $S$-wave two-nucleons and hypernuclear systems, this is the first time a stable $P$-wave
resonance has been found within this framework. 
%The scattering observables we calculate appear to be natural when compared with the fixed three body scale.
%
To supplement our ab initio calculation, we repeated it using the RGM, fixing as calculation input the $^3$H wavefunction using the density calculated with ab initio method.
The result found for the scattering parameter are qualitatively similar, but deviate from the results calculated using ab initio methods.
However, the uncertainty of the method is hard to be estimated a priori, both for the assumption of having a frozen core $^3$H and for the sensibility to the input wave function.
Nonetheless, the RGM results appear to be cut-off convergent and natural in the contact limit.
%

%
The values of the resonance energy and of the scattering parameters extracted from $S$-matrix formalism and from experiment can be hardly compared because of the very different way of extracting them, the different interpretation of the resonant state, and the difference among the experimental setups and protocol. 
However one can compare the $S$-matrix resonant poles among different theoretical calculations. \eftnopi find a resonance that is sharper than other calculations performed with realistic interactions. However, the calculations are still in agreement considering the \eftnopi LO truncation uncertainty. Comparing the result of different parametrizations of the EFT LO, namely starting from a two-body interaction that reproduces the deuterium binding energy or from a unitary interaction, we find a difference that is again in agreement with the expected uncertainty given by assuming a spin-independent interaction.
%
On the qualitative point of view, the major difference between \eftnopi and the resonances found in literature is the subthreshold nature (the resonance energy is lower than the threshold energy) of the former. 
However, this is not fundamentally a problem, in part because these pole can be physical\cite{formartinanyexample}, and because a non-subtreshold resonance may still be obtained introducing orders of the EFT expansion.
%

%
The possibility of creating $P$-wave many-body poles using a contact $S$-wave theory is remarkable in itself, but it also has strong implications for \eftnopi powercounting, possibly solving the issue of the absence of stable bound states states for nuclei larger than $^4$He at LO. We conjecture that an existing $P$-wave resonance might be moved on the stable region by the insertion of sub-leading orders, which would be trivially impossible if no $P$-wave states are present at all.

\section*{acknowledgement}
We thank Bira van Kolck for the patience, discussions, and mentoring about \eftnopi and halo EFT. 
MS was supported by the Pazy Foundation and the Israel Science Foundation grant 1086/21.
JK acknowledges the hospitality and support of The George Washington University and the helpful
conversations with H.~W.~Grie\ss hammer and N.~Walet.
LC an JC supported in part by the National Science Foundation under Grant No. NSF PHY-1748958.

\bibliographystyle{ieeetr}

%elsarticle-harv}
\bibliography{bibi.bib}

\end{document}

### 2022-06-18 manuscript/Draft_2.1.tex
from hexa

--- 2022-06-18 manuscript/Draft_0.4.tex
@@
 \address{Department of Physics, SRM University - AP, Amaravati 522502, Andhra Pradesh, India}
+\address{Theoretical Physics Division, School of Physics and Astronomy,\\
+  The University of Manchester, Manchester, M13 9PL, UK}
 
@@
 to bind larger nuclei like 16-oxygen can be cured in perturbation theory.
+
 \end{abstract}
@@
 expansion of the underlying scales and their interactions~\cite{Hammer:2019poc,Barnea:2013uqa}, and
-thereby provides a transparent framework to study the emergence of many-body phenomena from few-body properties.
-However, the nuclear incarnation of such a theory, Pionless effective field theory (\eftnopi), apparently fails to predict
+thereby provides a transparent framework to study the emergence of many-body phenomena
+from few-body properties.
+However, the nuclear incarnation of such a theory, pionless effective field
+theory (\eftnopi), apparently fails to predict
 stable bound states for $P$-shell
@@
 Whether or not the theory finds the physical bound state at LO veiled as a virtual or resonant state which
-reveals its physical character at higher orders is arguably the most imminent problem of the development of contact EFTs for
-Fermi systems.
-As perturbative higher-order insertions cannot create poles {\it ex novo}, the conceivable absence of such poles
-within the convergence radius of LO~\eftnopi~would make the theory in its current version useless for the description
-of larger nuclei.
-The challenge cast in simple words: Does the LO~\eftnopi~support any type of non-zero poles at complex momenta below its
-breakdown scale?
+reveals its physical character at higher orders is arguably the most imminent problem of the
+development of contact EFTs for Fermi systems.
+As perturbative higher-order insertions cannot create poles {\it ex novo},
+the conceivable absence of such poles
+within the convergence radius of LO~\eftnopi~would make the theory in its current version
+useless for the description of larger nuclei.
+The challenge cast in simple words: 
+Does the LO~\eftnopi~support any type of non-zero poles at complex momenta below its breakdown scale?
 
-Historically, resonances were studied in (A$\le$4)-body bosonic systems close to the unitary limit\cite{Deltuva:2012ig,deltuva2020energies} confirming the existence of a tower of Efimov resonances. 
-A recent study\cite{Habashi:2020qgw} proved the possibility of creating two-body $S$-shell resonances in the contact limit with negative effective range.%, naidon2017efimov}. 
-In the \eftnopi at LO framework, a resonance have been also found in neutral hypernuclear system $\Lambda nn$ \cite{Schafer:2020rba} and $S$-wave virtual states have been confirmed as exited states of triton \cite{Rupak:2019} and hypertriton \cite{Schafer:2020rba}.
-Finally, a recent study of $^3n$ confirmed the absence of $P$-wave resonance or virtual state in this system\cite{Dietz:2021haj}. 
-At the present knowledge of the authors, the calculations of $P$-shell systems stops at this level and no studies have been done for discrete invariant systems of equal mass.
-The major goal of this work is to study resonances in $^4$H a system never addressed before in this framework and that can be understood starting from its universal behavior. 
-The existence of an eventual $P$-shell resonance using \eftnopi at LO would open the possibility of finding the same structure also in heavier nuclei, with the chance of stabilizing many-nucleon systems by perturbative corrections.
+This issue has been addressed earlier for spatially symmetric states.
+Most prominently, a tower of so-called Efimov resonances is predicted in (A$\le$4)-body bosonic systems 
+when they approach the unitary limit~\cite{Deltuva:2012ig,deltuva2020energies}. 
+Even resonances corresponding to negative $S$-wave effective ranges have been found
+compatible with the zero-range theory~\cite{Habashi:2020qgw}.
+In the nuclear domain, LO~\eftnopi~finds resonances in the neutral
+hypernuclear system $\Lambda nn$~\cite{Schafer:2020rba}
+and $S$-wave virtual states in the triton~\cite{Rupak:2019} and hyper triton~\cite{Schafer:2020rba}. 
+For the spatially asymmetric wave function of $^3$n, in contrast, neither
+a $P$-wave resonance nor a virtual state
+were found~\cite{Dietz:2021haj}~cutoff-stable.
+In distinction to this latter finding where $^3$n represents a scale-free system,
+the subject of our study are channels affected by a finite three-body scale. 
+To the best of our knowledge, no simple and convincing argument
+can predict the existence of resonances under the aforementioned conditions
+solely from this three-body $S$-wave scale. 
+The smallest, and experimentally most interesting Fermi system which allows for
+a three-particle subsystem to be in a state with totally-symmetric internal wave function,
+while the total wave function of at least four particles
+must have one of the internal states occupied with two particles, is $^4$H, \ie, the subject of our study. 
+This systems acts as a benchmark for the usefulness of~\eftnopi~for a description of even heavier
+$P$-shell nuclei, and progress in understanding the nuclear chart beyond the $\alpha$ with
+non-perturbative two- and three-body contact interactions as a first approximation must address the
+resonant features of $^4$H.
+
+%
+Resonances in the $^4$H channel are expressed in n-$^3$H elastic cross sections~\cite{PhysRev.119.1981,SEAGRAVE1972250},
+$\pi^-$ absorption experiments~\cite{Sennhauser:1981tr,Gornov:1991fg}, and transfer reactions~\cite{Miljanic:1986zz,Sidorchuk:2003fwa}. 
+However, the extracted resonance parameters differ significantly and depend on the used experimental protocol as well as
+the underlying hypotheses in the data analysis. 
+For instance, from the results of one $\pi^-$+$^9$Be$\,\to\,$d+t+$^4$H
+experiment, multiple parameter sets for the lowest state
+($E_R=3.0\pm0.2$~MeV,~$\Gamma=4.7\pm1$~MeV)~\cite{Gornov:1991fg}, ($E_R=2.0\pm0.2$~MeV,~$\Gamma=1.2\pm0.2$~MeV)~\cite{Gurov:2005sp},
+and ($E_R=1.6\pm0.1$~MeV,~$\gamma^2=0.4\pm0.1$~MeV)~\cite{Gurov2005p}\footnote{$\gamma$ is a so-called reduced width~\cite{Gurov2005p}}
+were obtained. These three sets follow from the assumption of one, two, or three resonant states, respectively, being accountable for 
+the signal.
+An independent, albeit inconsistent R-matrix prediction fed with n-$^3$H cross sections~\cite{Tilley:1992zz}, yields
+a superposition of several resonant $P$-wave states with quantum numbers $J^\pi=0^-,1^-_I$, $1^-_{II},2^-$~\cite{Lazauskas:2004uq}~and
+groundstate parameters $E_R=3.2$~ MeV and $\Gamma=5.4$~MeV.
+%The discrepancies among different experimental approaches further increase when including the transfer reaction experiments.
+%
+
+Accurate numerical simulations of resonances in nuclear few-body systems employing system-appropriate interactions are
+non-trivial and limited to $A\leq6$~\cite{Li:2019pmg,Lazauskas:2019cxj}.  
+For certain channels comprising more nucleons, the usage of fragments which are inert at the considered scattering energies
+as effective cluster degrees of freedom allows for practical solutions~\cite{Arai:2003ek,deDiego:2007rd}.
+$^4$H resonances, in particular, have been studied in~\cite{deDiego:2007rd}~with an effective two-body n-$^3$H
+potential calibrated to p-$^3$He phase shifts. 
+The ensuing resonance energy was calculated either as an S-matrix pole or by performing a R-matrix analysis of the phase shifts.
+The resultant $1^-_I$ resonance-pole locations differ significantly: 
+$E_r=1.2$, $\Gamma=3.5$ MeV, and $E_r=3.6$, $\Gamma=5.3$ MeV, respectively. This discrepancy adds to the one mentioned in the previous
+paragraph, and resembles the {\it complexity} of analytically continuing a multi-channel S-matrix with numerous isolated and
+cut singularities.
+%
+% I dont know why this was removed, but it is the main point of the above paragraph
+%This result further enhances the difference between the position of the S-matrix pole 
+%and the resonance position extracted from the cross section, making difficult any kind 
+%of comparison between different calculations and experiments.
 %
@@
 %
-Experimentally, $^4$H resonances are clearly seen in n-$^3$H elastic cross sections \cite{PhysRev.119.1981,SEAGRAVE1972250}, as well as in $\pi^-$ absorption experiments \cite{Sennhauser:1981tr,Gornov:1991fg}, or in transfer reactions \cite{Miljanic:1986zz,Sidorchuk:2003fwa}.
-However, extracted resonance parameters differ substantially, depending on the used protocol and on the underlying hypothesis in the data analysis. 
-For instance, results of the same $\pi^-$+$^9$Be$\,\to\,$d+t+$^4$H experiment, performed by the same authors, yields for the lowest state ($E_R$=3.0$\pm$0.2~MeV, $\Gamma$=4.7$\pm$1~MeV) \cite{Gornov:1991fg}, ($E_R$=2.0$\pm$0.2~MeV, $\Gamma$=1.2$\pm$0.2~MeV) \cite{Gurov:2005sp}, and ($E_R$=1.6 $\pm$0.1 MeV, $\gamma^2$=0.4$\pm$0.1~MeV)\cite{Gurov2005p}, where $\gamma$ is the reduced width (see the original paper), depending whether one assumes the experimental signal to be created respectively by one, two, or three resonant states.
-Independently, the $R$-matrix analysis of n-$^3$H cross section \cite{Tilley:1992zz} concluded about a superposition of several $P$-waves resonant states with quantum numbers $J^\pi$=$0^-$,$1^-$,$2^-$.
-With two non-degenerate $J^\pi$=$1^-$ states (denoted $1^-_I$ and $1^-_{II}$ ) corresponding to two different total spin contributions in the asymptotic channels\cite{Lazauskas:2004uq}. 
-The lowest state parameters found in this case ($E_R$=3.2 MeV, $\Gamma$=5.4 MeV) are hardly compatible with the previous many-state analysis. 
-The discrepancies among different experimental approaches further
-increase when including the transfer reaction experiments.
-%
-
-From a numerical point of view, computing the $S$-matrix pole of a resonance is not an easy task. 
-Microscopic ab initio calculations for nuclear few-body systems are therefore not abundant and up to now have been performed for a limited amount of particles ($A<6$) \cite{Li:2019pmg,Lazauskas:2019cxj}.
-This limit is often circumvented by changing the calculation
-degrees of freedom and treating the many-body systems as a few-body problem between clusters as done in Ref.~\cite{Arai:2003ek,deDiego:2007rd} introducing approximations in the solution \cite{doweneedthis}.
-Resonances in $^4$H have been studied in the past, for example, in Ref.~\cite{deDiego:2007rd} using an effective two-body n-$^3$H potential adjusted to reproduce the $p$-$^3$He experimental phase shifts.
-Here, the resonance energy has been calculated either directly computing the $S$-matrix pole or by performing a $R$-matrix analysis of the phase shifts, showing a sensible difference among the two methods (the $1^-_I$ resonance is located at energy $E_r=1.2$, $\Gamma=3.5$ MeV, and $E_r=3.6$, $\Gamma=5.3$ MeV respectively).
-%
-% I dont know why this was removed, but it is the main point of the above paragraph
-This result further enhances the difference between the position of the S-matrix pole and the resonance position extracted from the cross section, making difficult any kind of comparison between different calculations and experiments.
-%
-Other calculations have been done in Refs.~\cite{Arai:2003ek,Horiuchi:2013iw,Lazauskas:2019cxj,Li:2021ado} using the resonating group method (RGM) with complex scaling, Spin-dipole strength functions, Faddeev-Yakubowski equations (FYE) in configuration space, and No-core Gamov Shell Model.
-The results differs from method to method varying in a range $E_R=\{0.9-3.6\}$ MeV and $\Gamma=\{1.0-5.3\}$ MeV.
-This variation appears to be a consequence of the different numerical techniques used more than on the interaction employed.
-In fact, studying the position of the resonance with different realistic interactions but the same theoretical scheme \cite{Lazauskas:2019cxj,Li:2021ado} leads to comparable results.
-
+Combining results obtained with the resonating-group method (RGM) and
+complex scaling, spin-dipole strength functions, 
+Faddeev-Yakubowski equations (FYE) in configuration space, and the
+no-core Gamov Shell Model~\cite{Arai:2003ek,Horiuchi:2013iw,Lazauskas:2019cxj,Li:2021ado}
+one obtains $E_R=\{0.9-3.6\}$ MeV and $\Gamma=\{1.0-5.3\}$ MeV. The uncertainty is dominated
+by numerical approximations while predictions within the same numerical framework are relatively
+insensitive to the kind of realistic interaction~\cite{Lazauskas:2019cxj,Li:2021ado}.
 %
@@
 
-In this letter, we study the emergence of a 3+1 $J^{\pi}=1^-$ resonance in $^4$H using LO \eftnopi, demonstrating the possibility of creating n$^3$H $P$-wave states using a purely $S$-wave contact interaction.
-In the region of resonance projectile neutron momentum is $\sim 0.5~m_\pi$, binding momenta of nucleons within $^3$H target are $\sim 0.4~m_\pi$ (for a combined distance from the complete disintegration threshold of $0.8~m_\pi$): thus $^4$H resonant states are at the limit of convergence of \eftnopi, nevertheless still observable in a LO calculation.
-The absence of any spin-orbit or tensor term in the LO interaction causes degeneracy between $J^{\pi}=0,^-,1^-_I,1^-_{II},2^-$ states which would be splitted including higher orders.
-As $^4$H can still be treated as both a four-body and two-cluster (triton-neutron) system, we choose to employ both the methodologies starting from the same nuclear Hamiltonian.
+The following report is a first step towards numerical-method and interaction-model-independent 
+predictions on the pole structure of $^4$H. While our approach (LO~\eftnopi) has innate uncertainties,
+it predicts the existence of a 3+1 $J^{\pi}=1^-$ resonance in $^4$H as an inevitable/universal feature of an almost
+unitary system with discrete scale invariance (three-body scale).
+
+% using LO \eftnopi, thus demonstrating the possibility of create n$^3$H $P$-wave states with purely $S$-wave contact interaction. 
+%In the region of resonance projectile neutron momentum is $\sim 0.5~m_\pi$, binding momenta of
+%nucleons within $^3$H target are $\sim 0.4~m_\pi$ 
+%(for a combined distance from the complete disintegration threshold of $0.8~m_\pi$): 
+%thus $^4$H resonant states are at the limit of convergence of \eftnopi, nevertheless still 
+%observable in a LO calculation. The absence of any spin-orbit or tensor term 
+%in the LO interaction causes degeneracy between $J^{\pi}=0,^-,1^-_I,1^-_{II},2^-$ states 
+%which would be splitted including higher orders. 
+%As $^4$H can still be treated as both a four-body and two-cluster (triton-neutron) 
+%system, we choose to employ both the methodologies starting from the same nuclear Hamiltonian.
+
+%% -> to the result section!
+We begin with a brief description of the interaction theory (LO~\eftnopi) before introducing the
+three numerical techniques which were used to reach our main conclusion. The results leading to that
+thesis are presented in the third part prior to a summary.
 
@@
 
-The theory used in this work is the \eftnopi\cite{vanKolck:1999mw} truncated at LO.
-The lowest order consists of contact two-body and a contact three-body interactions with corresponding low energy constants (LECs) fitted to reproduce physical observables.
-To further simplify the theory we truncate it around the SU(4) symmetry \cite{Konig:2016utl}.
+Nuclear dynamics in the unitary limit, and thereby their universal properties
+and correlations with quantum chromodynamics and atomic
+physics is described by the~\eftnopi\cite{vanKolck:1999mw}.
+From the leading order of this theory, \ie, a contact/zero-range theory,
+we deduce our conclusions, and therefore need to introduce its structure. 
+It comprises one\footnote{We assume SU(4) symmetry~\cite{Konig:2016utl}~
+and thus degenerate singlet and triplet nucleon-nucleon channels.}
+two- and a three-body contact interaction, each 
+associated with an independent low energy constant (LEC).
 %the theory is perturbative around su(4) symmetry, so we do not assume but we truncate it
-Therefore, $NN$ spin-singlet and spin-triplet interactions are identical and only one contact term appears in the two-body sector.
-This adds further uncertainty to the theory of order $(a_0m_{\pi})^{-1}\sim30\%$ on the top of the usual \eftnopi LO truncation error.
-The contact interactions are regularized by an introduction of a Gaussian regulator and a momentum cut-off $\Lambda$.
-This yields two- and three-body potential
+%Therefore, $NN$ spin-singlet and spin-triplet interactions are identical and only one contact term appears in the two-body sector.
+This interaction implies an uncertainty of order $(a_0m_{\pi})^{-1}\sim30\%$.
+For the numerical calculations, we find regularization 
+with a Gaussian function of width $\propto\Lambda^{-1}$ convenient.
+In coordinate representation, the two- and three-body
+potentials defined from the bare vertices are:
 %
 \begin{equation}
-    V(\textbf{r})=C_0 \sum_{i,j}^N e^{-\frac{r_{ij}^2\Lambda^2}{4}},
+    \hat{V}=C_0 \sum_{i<j}^N e^{-\nicefrac{r_{ij}^2\Lambda^2}{4}}
+    \quad,
+\label{eq:vnn}
 \end{equation}
@@
 \begin{equation}
-    W(\textbf{r})=D_0 \sum_{ijk}^N \left[
-    e^{-\frac{(r_{ij}^2+r_{ik}^2)\Lambda^2}{4}}+
-    e^{-\frac{(r_{ij}^2+r_{jk}^2)\Lambda^2}{4}}+
-    e^{-\frac{(r_{jk}^2+r_{ik}^2)\Lambda^2}{4}}\right],
+    \hat{W}=D_0 \sum_{i<j<k}^N \left[
+    e^{-\nicefrac{(r_{ij}^2+r_{ik}^2)\Lambda^2}{4}}+
+    e^{-\nicefrac{(r_{ij}^2+r_{jk}^2)\Lambda^2}{4}}+
+    e^{-\nicefrac{(r_{jk}^2+r_{ik}^2)\Lambda^2}{4}}\right]
+    \quad.
+\label{eq:vnnn}
 \end{equation}
 %
-where the cut-off dependent LECs ($C_0$ and $D_0$) are fitted on two-body observables and triton binding energy ($B_3=8.48$~MeV). 
-In order to assess the uncertainty introduced by the adoption of SU(4) symmetry, we use two different parametrizations for the two-body LEC $C_0$: one at unitarity (with $|a_0|>10^5$~fm and referred to as ``unitary'') and one fitting the deuteron binding energy $B_2=2.22$~MeV (referred as ``nuclear'').
-We assume a degenerate nucleon mass $m=938.858$ MeV.
+The LECs ($C_0$ and $D_0$) are renormalized by fixing the two-body
+and triton binding energies.
+While the latter is constrained to $B_3=8.48$~MeV, 
+we the uncertainty introduced of the SU(4) approximation with two
+different conditions on the two-body ground state:
+first, we demand an almost zero-energy state with $|a_0|>10^5$~fm to
+approximate the unitary limit
+(``unitary'' case), and second, we calibrate $C_0$ to the physical deuteron
+binding energy $B_2=2.22$~MeV
+(``nuclear'' case). All nucleons are assumed to have mass $m=938.858$~MeV.
 
-To extract the effective range parameters and resonance energy we employ and compare results of three different methods.
-We use two ab initio techniques (four-body calculations): the direct solution of the Faddeev-Yakubovsky equations (FYE) in configuration space \cite{Lazauskas:2004hq, Lazauskas:2019hil} and the stochastic variational methods (SVM)\cite{Suzuki:1998bn};
-and a potential folding technique that reduces the problem into effective two-body problem, represented by neutron impinging on a solid triton core.
+Effective-range parameters and resonance energies are extracted from solutions of the Schr\"odinger equation, defined with
+this potential, with three different methods:
+Faddeev-Yakubovsky equations (FYE) in configuration space~\cite{Lazauskas:2004hq, Lazauskas:2019hil}, the stochastic variational method
+ (SVM)~\cite{Suzuki:1998bn}, and a potential-folding technique which obtains an effective two-body problem of a neutron scattering off
+ an inert triton core.
 
-Employing the above interaction we extract the triton-neutron scattering parameters ($a_L$ and $r_L$) for $L=0$ and $L=1$ trough the effective range expansion (ERE) expanded around the triton-neutron threshold:
+For the triton-neutron scattering parameters ($a_L$ and $r_L$) in relative $L=0$ and $L=1$ partial waves, we use
+the effective range expansion (ERE) about the triton-neutron threshold:
 %
 \begin{equation}
-    k^{2L+1}\text{cot}(\delta_L)=-\frac{1}{a_L}+\frac{1}{2}r_L k^2 + ... \, ,
+    k^{2L+1}\cot\delta_L=-\frac{1}{a_L}+\frac{1}{2}r_L k^2 + ... 
+    \quad ,
     \label{eq.app.ere}
@@
 %
-where $\delta_L$ is the triton-neutron phase-shift at angular momentum $L$ and $k$ is the center of mass momentum of the fragments. 
-Resonances will, therefore, emerge as poles of the system's $T$-matrix
+where $\delta_L$ is the triton-neutron phase shift at angular momentum $L$, and $k$ is the relative momentum of the fragments in the center-of-mass frame. 
+Resonances of the system's $T$-matrix are found as complex roots of the denominator of
 %
 \begin{equation}
-T =\frac{4\pi}{m}\frac{1}{\text{cot}(\delta)-i} =
-\frac{4\pi}{m}\frac{k^{2L+1}}{\frac{1}{a_L}+...+\frac{1}{2}r_L k^2
--ik^{2L+1}} \label{eq:Tmatrix}
+T =\frac{4\pi}{m}\cdot\frac{1}{\cot\delta-i} =
+\frac{4\pi}{m}\cdot\frac{k^{2L+1}}{-\frac{1}{a_L}+...+\frac{1}{2}r_L k^2
+-ik^{2L+1}}
+\quad.
+\label{eq:Tmatrix}
 \end{equation}
 %
-and can be extracted either by fitting phase shifts to the ERE formula or directly through solving the Schr\"odinger equation for complex energies.
+
+From the FYE (see~\eqref{eq:FYe_res}~below) we obtain the amplitude directly for complex momenta and
+search for its poles near the axes. In contrast, the SVM and the RGM calculate $\cot\delta$ for number of real
+momenta approaching $0~$MeV. This series of points is fit to the ERE~\eqref{eq.app.ere} up to second order.
+Resonances are then identified with those roots of the polynomial $-ik^{2L+1}$ which lie in the third and forth quadrant
+of the complex energy sheet.
+%and can be extracted either by fitting phase shifts
+% to the ERE formula or directly through solving the Schr\"odinger equation for complex energies.
 %
-From an theoretical point of view, extracting the resonance energy with the two methods is not equivalent. 
-Solving the Schr\"odinger equation for complex energies is affected by the \eftnopi LO truncation error ($\Gamma_{\eftnopi}\approx k_{res}/m_\pi\sim80\%$), while extracting the resonance position using the ERE of the triton-neutron phaseshift and using RGM formalism (see below) is equivalent to the halo-EFT expanded around t-n treshold.
-In the latter case, a new scale, the breaking momentum of $^3$H, is introduced at momentum $K_{d-n}\simeq94$ MeV. 
-Since the scattering parameters are extracted using \eftnopi at LO we expect the two methods to agree inside the truncation error $\Gamma_{Halo}\approx k^*_{res}/K_{d-n}\simeq70\%$ using only the scattiring volume and $\Gamma_{Halo}^2$ %should be square, but if someone recheck is better
-if the effective range $r_1$ is also included in the ERE.
+The uncertainties in the predicted pole locations and ERE parameters thus differ from method to method. 
+%From an theoretical point of view, extracting the resonance energy with the two methods is not equivalent.
+The theoretical uncertainty in the SVM and FYE calculations is expected to decrease with the convergence rate
+of the pionless theory, namely, $\approx k_{\rm typ}/m_\pi\sim80\%$ with a typical momentum set by the
+resonance location $k_{\rm res}$ (see results).
+%Solving the Schr\"odinger equation for complex energies is affected by the
+% \eftnopi LO truncation error ($\Gamma_{\eftnopi}\approx k_{res}/m_\pi\sim80\%$),
+%  while extracting the resonance position using the ERE of the triton-neutron
+%   phaseshift and using RGM formalism (see below) is equivalent to the halo-EFT expanded around t-n treshold.
+The breakdown scale, and thus the convergence rate of the RGM is set by the lowest excitation threshold of $^3$H.
+%In the latter case, a new scale, the breaking momentum of $^3$H, is introduced at momentum 
+We associate a momentum $k_{d-n}\equiv\sqrt{\nicefrac{4}{3}\, m\,(B_3-B_2)}\simeq94$ MeV with this excitation.
+With this smaller area of applicability of the cluster/RGM formulation, a pole predicted at some $k_{\rm res}\approx k_{d-n}$
+with the SVM or FYE, whose breakdown is around $m_\pi$, might not be seen with the RGM. In fact, this difference in convergence radii
+along with the relatively large uncertainty of $\sim80\%$ explains the results which we will discuss
+after the following details on the numerical methodology.
 
-\vspace{2mm}
+%Since the scattering parameters are extracted using \eftnopi at LO
+% we expect the two methods to agree inside the truncation error
+% $\Gamma_{Halo}\approx k^*_{res}/K_{d-n}\simeq70\%$ using only
+% the scattiring volume and $\Gamma_{Halo}^2$ %should be square, but if someone recheck is better
+%if the effective range $r_1$ is also included in the ERE.
 
 %================================================
-\subsection{Faddeev-Yakubovsky equation formalism}
+\subsection{Faddeev-Yakubovsky-equation formalism}
 %================================================
 
-This formalism, as well as our employed numerical techniques, have been described in detail in Refs.~\cite{Lazauskas:2004hq,Lazauskas:2019hil}.
-Here we will just stress that, in order to determine n-$^3$H scattering lengths (volumes), we solve the differential FYE equations by requiring the systems wave function to satisfy boundary condition in the far asymptote for retrieving neutron, defined by:
+The Faddeev-Yakubovsky formalism decomposes the few-body Schr\"odinger/Lippman-Schwinger equation into a
+set of equations in order to organize the overlapping spectra and divergences of the few-body scattering 
+problem. Details about this complex and on our particular numerical realization can be found in
+Refs.~\cite{Lazauskas:2004hq,Lazauskas:2019hil}.
+The appropriate boundary conditions on the formalism which yield the n-$^3$H scattering lengths (volumes)
+relevant for this work,
 %
 \begin{equation}
-\begin{split}
-\Psi(X_{^3{\rm H}},\vec{y}_{n-^3{\rm H}})=&\lim_{k\rightarrow0}\psi_t(X_{^3{\rm H}})\big([j_L(k|y_{n-^3{\rm H}}|)/k^{L}]\\
-&+a_L(k) [n_L(k|y_{n-^3{\rm H}}|)k^{L+1}]\big)Y_L(\hat{y}_{n-^3{\rm H}});  \label{eq:FYe_a}
-\end{split}
+\Psi(t,\ve{y})=\lim_{k\rightarrow0}\,\left(\psi_t\,\left[j_L(ky)/k^{L}+a_L(k)\, n_L(ky)k^{L+1}\right]\,Y_L(\hat{\ve{y}})\right)
+\quad,  \label{eq:FYe_a}
 \end{equation}
 %
-here $j_L(z)$ and $n_L(z)$ are spherical Bessel functions of the first and second kind respectively. 
-$\psi_t(X_{^3{\rm H}})$ is the wave function of the $^3$H ground state, which is found before undertaking n-$^3$H scattering calculations. 
-In the particular case of determining the scattering lengths (volumes) $a_L$, calculations are performed for vanishing momenta $k$.
-Note that, in the limit $k\rightarrow0$, the expressions in the brackets are finite functions depending on a distance $|y_{n-^3{\rm H}}|$.
+fix the solutions of the differential FYE equations in the far asymptote where the radial distance $\left|\ve{y}\right|$
+between the neutron and $^3$H is larger than the support of $\hat{V}$ and $\hat{W}$.
+Here, $j_L(z)$ and $n_L(z)$ are spherical Bessel functions of the first and second kind,
+respectively, and 
+$\psi_t$ is the $^3$H ground-state wave function whose determination precedes n-$^3$H scattering calculations. 
+wERE parameters are extracted in the limit $k\to0~$MeV.
+In this limit, both terms in the bracket remain finite functions of a distance $|y_{n-^3{\rm H}}|$.
 
-To determine positions of the resonant states we solve FYE by imposing slightly different boundary condition for neutron asymptote:
+Resonant states are obtained by imposing the canonical boundary conditions on the FYE, namely a purely outgoing wave
+in the region where the neutron projectile is no longer interacting with any target $^3$H nucleons:
 \begin{equation}
-\begin{split}
-\Psi(X_{^3{\rm H}},\vec{y}_{n-^3{\rm H}})=&\psi_t(X_{^3{\rm H}}) \big(h_L^+(k_{r}|y_{n-^3{\rm H}}|)\\
-&+F_L(k_r)h_L^-(k_{r}|y_{n-^3{\rm H}}|)\big) Y_L(\hat{y}_{n-^3{\rm H}});  \label{eq:FYe_res}
-\end{split}
+\Psi(t,\ve{y})=\psi_t\,\left[h_L^+(k_{\rm res}y)+F_L(k_{\rm res})h_L^-(k_{\rm res}y)\right]\,Y_L(\hat{\ve{y}})
+\quad.  \label{eq:FYe_res}
 \end{equation}
-here $h_L^-(z)$ and $h_L^+(z)$ are Spherical Bessel functions of the third kind.
-Complex momentum plane $k_r$ is scanned to find positions where the function $F_L(k_r)$ vanishes and thus wave function $\Psi(X_{^3{\rm H}},Y_{n-^3{\rm H}})$ represents purely outgoing n-$^3$H waves.
+Now, $h_L^-(z)$ and $h_L^+(z)$ are Spherical Bessel functions of the third kind, and 
+the solution corresponds to a resonant state for those complex momenta $k_{\rm res}$ at which the
+function $F_L(k_{\rm res})$ vanishes, \ie, where the wave function $\Psi(t,\ve{y})$ represents
+a purely outgoing n-$^3$H waves.
 
 %================================================
-\subsection{Harmonic oscillator trap}
+\subsection{Harmonic-oscillator-trapped SVM}
 %================================================
-The second microscopic approach involves an introduction of the Harmonic oscillator (HO) trapping potential
+The so-called Stochastic Variational Method~\cite{Suzuki:1998bn} (SVM) obtains the spectrum of a
+non-relativistic few-body Hamiltonian in a high-dimensional, yet finite, basis of normalizable,
+Gaussian-type functions. One way to utilize this method, despite the difference in asymptotic
+behavior of the basis states and scattering wave functions for a description of the latter, is to
+augment the physical interaction potential between the four particles~\eqref{eq:vnn},\eqref{eq:vnnn}~with
+an auxiliary harmonic-oscillator (HO) trap:
+%
 \begin{equation}
-    V_{\rm HO}(\textbf{r}) = \frac{m}{2A} \omega^2 \sum_{i<j} (\textbf{r}_i - \textbf{r}_j)^2
+    \hat{V}_{\rm HO} = \frac{m\,\omega^2}{2A} \sum_{i<j} (\textbf{r}_i - \textbf{r}_j)^2
+\quad.
 \end{equation}
-with oscillator frequency $\omega$ into $A=4$-body $^4$H system.
-
-Assuming that the range of an interaction is much smaller than the typical HO trap range $R << b_{\rm HO} =\sqrt{2/(m \omega)}$ one can match asymptotic $n ^3$H part of a trapped $^4$H wavefunction to the trapped solution of effective $n ^3$H two-body system with no nuclear interaction considered.
-The $n ^3$H phasehifts $\delta_L$ at relative momentum $k$ are then extracted using generalized Bush formula for an arbitrary orbital momentum $L$ \cite{Suzuki:2009}
+%
+For an interaction whose range is significantly shorter than the typical HO trap range $R << b_{\rm HO} =\sqrt{2/(m \omega)}$,
+associated with the oscillator frequency, an asymptotic interval exists in which the relative motion between
+the neutron and $^3$H is not a free, non-normalizable wave, but a combination of harmonic-oscillator eigenfunctions.
+These new asymptotic states are normalizable themselves and thus amenable for an expansion in the SVM basis.
+The phase shifts $\delta_L(k)$ for a neutron scattering off $^3$H with momentum $k$ are then extracted
+using the generalized Busch formula~\cite{busch1998two}~which is valid for any orbital angular momentum $L$~\cite{Suzuki:2009}:
 
 \begin{equation}
-    (-)^{L+1} \left(\sqrt{4\mu \omega}\right)^{2L+1} \frac{\Gamma\left(3/4 + L/2 - \epsilon^n_\omega/2\omega\right)}{\Gamma\left(1/4 - L/2 - \epsilon^n_\omega/2\omega\right)} = k^{2L+1}~{\rm cot}\left(\delta_L \right),
+    (-)^{L+1} \left(\sqrt{4\mu \omega}\right)^{2L+1} \frac{\Gamma\left(3/4 + L/2 - \epsilon^n_\omega/2\omega\right)}{\Gamma\left(1/4 - L/2 - \epsilon^n_\omega/2\omega\right)} = k^{2L+1}~\cot\delta_L
+    \quad,
 \end{equation}
-where $ k=\sqrt{2\mu \epsilon^n_\omega}$, $\Gamma(x)$ is a Gamma function, $\mu \simeq 3/4 m$ denotes $n ^3$H reduce mass, and $\epsilon^n_\omega = E_\omega (^4{\rm H})-E_\omega (^3{\rm H})$ is an energy of the $n$-th $^4$H excited state in a trap with respect to the $n ^3$H threshold.
-Here, bound state energies $E_\omega (^3{\rm H})$, $E_\omega (^4{\rm H})$ are calculated using Stochastic Variational Method \cite{Suzuki:1998bn}.
-Both $S$-wave ($L=0$) and $P$-wave ($L=1$) $n ^3$H phaseshifts are extracted applying HO trap lengths $40~{\rm fm} \leq b_{\rm HO} \leq 60$~fm.
+with $k=\sqrt{2\mu \epsilon^n_\omega}$, $\Gamma(x)=\int_0^\infty z^{x-1}e^{-z}dz$, reduced mass $\mu \simeq 3/4 m$.
+$\epsilon^n_\omega = E_\omega (^4{\rm H})-E_\omega (^3{\rm H})$ is the energy of the $n$-th excited $^4$H state in a trap
+with respect to the n-$^3$H threshold. The bound-state energies $E_\omega (^3{\rm H})$, $E_\omega (^4{\rm H})$ are
+calculated consistently with the SVM in the absence of the trapping potential.
+The $S$-wave ($L=0$) and $P$-wave ($L=1$) n-$^3$H phase shifts of interest are then found within an interval of HO trap lengths
+$40~{\rm fm} \leq b_{\rm HO} \leq 60$~fm.
+
+\begin{figure*}
+\centering
+  \centering
+  \includegraphics[width=\linewidth]{Graphs/ere.pdf}
+  \caption{Cutoff and numerical-technique dependence of LO~\eftnopi~predictions
+  for the leading two effective-range parameters (left panel: $S$-wave scattering length $a_0$ and effective range $r_0$;
+   right panel: $P$-wave scattering volume $a_1$ and $r_1$)
+   of the n-$^3$H scattering amplitude
+  (SVM + Busch/Faddeev-Yakubovsky: red circle; 2-fragment RGM: blue triangle).
+ The zero-range limit $\Lambda \rightarrow \infty$ (dashed lines) fits~\eqref{extrapolation}~to the discrete results
+ (fit uncertainty: shaded bands).
+ }
+  \label{fig:ERE_Parameters}
+\end{figure*}
 
@@
 %================================================
-Finally, the RGM technique was used to fold the two- and three-body interactions between the three particles in $^3$H and
-the neutron in an effective n-$^3$H potential.
-This is done assuming that the $^3$H wave-function can be approximated as a sum of single Gaussians and that the scattering process happens at low energy such that no excitation can be created.
-%
-The input of this procedure is the $^3$H wave function, which has been extracted as the square root of the three-body single-particle density distribution calculated using the SVM. 
-A linear combination of 5 Gaussians was used to parametrize the $^3$H wavefunction (the number of Gaussians was increased up to 8 without appreciable changes in the results). 
-The requirement of having as input the wave function of the cluster makes the method dependent (and the result sensible) on a microscopic calculation. 
-However, the possibility of transforming a four-fermion scattering problem into a simpler two-body problem is considered advantageous.
-%
-On one hand, the RGM potential loses some of the microscopic symmetries of the initial Hamiltonian, namely, it is non-local, energy-dependent, and non-Hermitian. 
-On the other, the folded two-body scattering problem can be solved numerically relatively easily with the finite difference method.
-The method is also scalable and can be applied to larger systems in which microscopic scattering calculations are prohibitive.
-%
-Moreover, and beyond the simplification of the many-body scattering calculation, RGM also allows for simple visualization
-of the effective cluster-particle interaction (after a particular regulator and cut-off configuration is chosen).
-%
-%\highlight{The details of the folding procedure and the folded interaction can be found in the attached document.}
+For neutron-projectile momenta much smaller than any excitation
+scale of the triton, $k\ll k_{d-n}$, the description
+of n-$^3$H scattering with a halo EFT~\cite{Hammer:2022lhx}~becomes appropriate. 
+The resonating-group expansion
+of the four-body wave function
+resembles the accompanying transition from nuclear (``microscopic'') 
+degrees of freedom to a fundamental trimer ($^3$H) and an atom (neutron)
+field. Halo EFTs must account for exchange effects between particles within 
+their elemental fields, \eg,
+the Pauli repulsion between the projectile neutron and one of the neutrons 
+inside the triton, via renormalization constraints, \ie,
+through the introduction of, possibly redundant, (n-$^3$H)-interaction vertices.
+The so-called resonating-group method can be employed such that its expansion of 
+the wave function in a double
+product of fragment-internal ($\phi$) and relative ($\chi$) states: 
+\begin{equation}
+\Psi=\sum_{a_j}\prod_{m=1}^{a_j}\phi^j_m\prod_{n=1}^{a_j-1}\chi^j_n\quad,
+\end{equation}
+and variations $\delta\Psi$ thereof, becomes formally identical to a cluster EFT. 
+The compound fields of the halo EFTs
+are identified with cluster states $\phi^j$ of a given partition $a_j$ of the $A$ 
+nucleons, and the effective vertices
+of the EFT are expressed in a set of integral kernels. Deriving the latter is 
+tantamount to matching the halo EFT with
+a microscopic, few-body description, and we achieve this matching analytically.
+
+In short, we utilize the technique with the same boundary conditions as in the FY 
+approach~\eqref{eq:FYe_a} but find solutions
+to the four-body Schr\"odinger equation in a subspace in which only variations 
+of the relative function between the
+triton-core $\psi_t$ and the neutron are admitted. Therefore 
+(see~\cite{wildermuth1977unified}~for a pedagogical exposition),
+the four-body problem reduces to a two-body for the relative 
+motion between the triton and neutron.
+With a Gaussian expansion of the core, the Gaussian regulated 
+EFT potentials translate analytically into an effective
+core-atom interaction with a local and a non-local, energy-dependent 
+component which fully account for the identity and associated
+permutation properties of the neutron projectile and its core copy:
+
+\begin{equation}
+\left(\hat{T}_{\rm rel}-E+\hat{U}^{(2)}_{\rm eff}(\ve{y})\right)\chi(\ve{y})+
+\int\hat{U}^{(3)}_{\rm eff}(\ve{y},\ve{y}',E)\chi(\ve{y}')d\ve{y}'=0
+\quad.\label{eq:rgm_sgl}
+\end{equation}
+
+No additional renormalization of the effective triton-neutron potentials 
+is required, and we obtain their dependence
+on $C_0$~\eqref{eq:vnn}~ and $D_0$~\eqref{eq:vnnn}~by analytically 
+integrating out fast, \ie, core-internal degrees of freedom.
+In effect,~\eqref{eq:rgm_sgl}~represents a halo EFT with two degrees of freedom: the extended but inert triton
+and a neutron, with an interaction parametrized by the fundamental, nuclear theory.
+A necessary matching constraint between the two descriptions is the wave function of the three-nucleon state, \ie, the core.
+%This regulator dependent object is one source of numerical uncertainty.
+To satisfy this constraint, we feed the single-particle 
+densities of the SVM calculation
+to the RGM integration over the fast degrees of freedom, thereby obtaining $\hat{U}^{(2/3)}_{\rm eff}$
+as functions of the expansion coefficients of these densities in a set of
+$\leq8$ Gaussian functions.
+
+It remains to solve the integro-differential equation~\eqref{eq:rgm_sgl}, 
+which is projected into partial waves, and we obtain the relative $S$- and $P$-wave functions
+via a standard finite-difference method. The amplitude 
+$a_L(k)$ is subsequently found with boundary conditions identical to~\eqref{eq:FYe_a},
+albeit, for real momenta, only.
+Although the numerical accuracy for the predictions of
+ERE parameters and pole locations in this approach is inferior to the four-body formulations
+due to the smaller breakdown momentum $k_{d-n}$, any divergence of an unrenormalized
+amplitude or the convergence to zero, which the four-body problem might exhibit,
+will be apparent in the RGM formulation.
 
@@
 
-\begin{figure*}
-\centering
-  \centering
-  \includegraphics[width=\linewidth]{Graphs/ere.pdf}
-  \caption{Left panel : $S$-wave scattering length $a_0$ and effective range $r_0$ calculated using microscopic techniques, SVM with Bush Formula and solving the Faddeev-Yakubovsky equation (red), and n$^3$H folding using RGM (blue) for the "nuclear" case.
-Right panel : the same as in the left panel but for $P$-wave scattering parameters - scattering volume $a_1$ and $P$-wave effective range $r_1$.
-For each scattering parameter the corresponding dashed line represents an extrapolation to the contact limit ($\Lambda \rightarrow \infty$) using the function in eq.~\ref{extrapolation}.
-The extrapolated values together with extrapolation uncertainties are shown by the shaded bands.}
-  \label{fig:ERE_Parameters}
-\end{figure*}
-
-We examine the scattering parameters of the n$^3$H system calculated with the microscopic methods (SVM with Bush Formula and solving the Faddeev-Yakubovsky equation). 
-For scattering lengths $a_0$ and volumes $a_1$ we find relative agreement between two microscopic methods of order $\simeq 0.1-1 \%$ for $a_0$ and $\simeq 1-10\%$ for $a_1$ between the results. 
+We shall first analyze the predictions of LO~\eftnopi for relative momenta in the n-$^3$H scattering system close to zero.
+There, an ERE expansion of the amplitude is appropriate, and we extract its parameters with the microscopic methods 
+(SVM + Busch Formula and FYE) as described above. 
+For the scattering length $a_0$ and volume $a_1$,
+we find relative agreement between two microscopic methods of order $\simeq 0.1-1 \%$ for $a_0$ and $\simeq 1-10\%$ for $a_1$ between the results. 
 The effective ranges in $S$-wave ($r_0$) and $P$-wave ($r_1$) were extracted only via Bush formula and their numerical errors are not larger than $0.1$~fm and $0.1$~fm$^{-1}$, respectively.
@@
 %
+
+%
 In line with the sign convention adopted in eq. \ref{eq.app.ere}, the positive $a_0$ values suggest repulsive $S$-wave interaction, indicating dominance of Pauli principle between neutrons. 
@@
 %
-Comparing the ``unitary'' with the "nuclear" cases, both repulsion in $S$-wave and attraction in $P$-wave are preserved, however, for the former, the $a_0$ and $a_1$ are smaller in magnitude, which suggests in general weaker n$ ^3$H interaction in the "unitary" case.
+
+%
+Comparing the ``unitary'' with the "nuclear" cases, both repulsion in $S$-wave and attraction in $P$-wave are preserved, however, for the former, the $a_0$ and $a_1$ are smaller in magnitude, which suggests in general weaker n-$^3$H interaction in the "unitary" case.
 %
@@
 %
+
+\begin{figure*}
+\centering
+\includegraphics[width=\textwidth]{./Graphs/rgm}
+%\includegraphics[width=.39\textwidth]{./Graphs/rgm_potential_unit}
+%\hfill
+%\includegraphics[width=.60\textwidth]{./Graphs/NonLocPot10_nuc}
+\caption{Left panel: Local part of the effective $P$-wave n-$^3$H interaction $V(r,r')\delta(r'-r)$ as a function of the distance between the neutron and the center of mass of the triton.
+The interaction is extracted using the RGM at the n-$^3$H zero energy and evaluated for different cut-offs from 1.5 (red line) to 10~fm$^{-1}$ (blue line); intermediate cut-offs are shown as green dashed lines.
+Right panel: Same as in the left panel but full non-local $V(r,r')$ interaction calculated for cutoff $\Lambda=10$~fm$^{-1}$.}\label{Fig:Potential}
+\end{figure*}
 
@@
 %
-\begin{figure*}
-\centering
-\includegraphics[width=.39\textwidth]{./Graphs/rgm_potential_unit}
-\hfill
-\includegraphics[width=.60\textwidth]{./Graphs/NonLocPot10_nuc}
-\caption{\edit{change the capital R on left pannel and make sure it is the nuclear case}Left panel: Local part of the effective $P$-wave n$^3$H interaction $V(r,r')\delta(r'-r)$ as a function of the distance between the neutron and the center of mass of the triton.
-The interaction is extracted using the RGM at the n$^3$H zero energy and evaluated for different cut-offs from 1.5 (red line) to 10~fm$^{-1}$ (blue line); intermediate cut-offs are shown as green dashed lines.
-Right panel: Same as in the left panel but full non-local $V(r,r')$ interaction calculated for cutoff $\Lambda=10$~fm$^{-1}$.}\label{Fig:Potential}
-\end{figure*}
 
@@
 %
-Although the effective n$^3$H interaction is not observable, we use the RGM to extract its $P$-wave
+Although the effective n-$^3$H interaction is not an observable, we use the RGM to extract its $P$-wave
 component to acquire a deeper insight into interplay between repulsive and attractive parts and their evolution with $\Lambda$.
 In fig.~\ref{Fig:Potential}, we visualise such interaction for the "nuclear" case and zero-energy scattering.
+%
+
+%
 On the left panel, the local part of the coordinate space interaction ($r=r'$) is shown as a function of the distance between the neutron and the center of mass of the triton. 
 A positive energy pocket at distance $r\simeq0.5$~fm can be noticed for small cut-offs, however, it vanishes approaching the contact limit ($\Lambda\to\infty$). 
+Remarkably, with only the local part of interaction, no resonance can emerge.
+%
+
+%
 On the right panel, the full coordinate interaction $V_{n-t}(r,r')$ is plotted for $\Lambda=10$~fm$^{-1}$ and zero energy.
@@
 %
-So far our calculations revealed non-vanishing $P$-wave attraction in n$^3$H scattering in the contact limit, suggested by the negative $a_1(\infty)$, and the existence of attractive pocket in the effective n$^3$H $P$-wave RGM potential which persists even at highest considered cut-off $\Lambda=10$~fm$^{-1}$.
+So far our calculations revealed non-vanishing $P$-wave attraction in n-$^3$H scattering in the contact limit, suggested by the negative $a_1(\infty)$, and the existence of attractive pocket in the effective n$^3$H $P$-wave RGM potential which persists even at highest considered cut-off $\Lambda=10$~fm$^{-1}$.
 Both of these results lead us, yet still not quite firmly, to an existence of a broad $^4$H resonance stabilizing with increasing momentum cut-off.
-Consequently, the final step in our calculation is to search directly for a position of the $J^\pi=1^-$ nuclear resonance looking for a pole of a 4-body $S$-matrix.
-This has been done by solving the Faddeev-Yakubovsky equations by imposing divergent boundary conditions provided by outgoing n$^3$H wave behavior.
+%
 
-In the left panel of fig.~\ref{fig:Pole_PositionN}, the evolution of such pole using the ``nuclear'' interaction is shown in the complex energy plane.
+%
+The final step in our calculation is to search directly for a position of the $J^\pi=1^-$ nuclear resonance looking for a pole of a 4-body S-matrix.
+This has been done by solving the Faddeev-Yakubovsky equations.
+Results are are displayed in fig.~\ref{fig:Pole_PositionN}.
+In the left panel, the pole trajectory as function of the cutoff, using the ``nuclear'' interaction, is shown in the complex energy plane. 
 It can be followed to pass the n$^3$H threshold energy $B_{t}=8.484$~MeV (denoted by dashed vertical line) finally stabilizing around $E^{res}=-8.7-i\,3.1$ for cutoffs greater than $6$~fm$^{-1}$.
@@
 %
-Comparing our $^4$H resonance result with experimental data and previous calculations, the major difference is that our pole goes to the subthreshold region in the $\Lambda\rightarrow\infty$ limit, namely, the resonance energy is lower than the n$^3{\rm H}$ threshold energy (notice that this kind of states are different than boundstates and remain non normalizable).
+Comparing our $^4$H resonance result with experimental data and previous calculations, the major difference is that our pole goes to the subthreshold region in the $\Lambda\rightarrow\infty$ limit, namely, the resonance energy is lower than the n$^3{\rm H}$ threshold energy.
+Notice, however, that this kind of states are not bound despite their negative energy, and remain non normalizable.
 Theoretically, this is not an issue since the pole existence in subthreshold region does not break causality and it can be moved in the standard resonant region by a continuous transformation of the interaction (e.g.
-reversing the renormalization group transformation) and by the inclusion of \eftnopi subleading orders.
+reversing the renormalization group transformation) and, possibly, by the inclusion of \eftnopi subleading orders.
 % I dont like this statement bc the LO is compatible with a normal resonance and we expect this pole to go in the correct physical position at a certain point in the pionless expansion
@@
 %
-To stress this point, one can notice that the $S$-matrix pole energy is, in general, lower than the one extracted with $R$-matrix analysis.
+To stress this point, one can notice that the S-matrix pole real part of the energy is, in general, smaller than the one extracted with R-matrix analysis.
 An illustrative example is provided by the  transfer reactions $^2$H(t,p)$^4$H and $^3$H(t,d)$^4$H \cite{Sidorchuk:2004ntw}. 
-The $R$-matrix analysis of the results obtains for the lowest $^4$H state $E_R$=3.05$\pm$0.19 MeV and $\Gamma$=4.18$\pm$1.02 MeV while the corresponding $S$-matrix pole, extracted by the same authors, led to $E_R$ =1.99$\pm$0.37 MeV and $\Gamma_R$=2.85$\pm$0.3 MeV.
-Therefore, a fair comparison can only be done with other $S$-matrix pole predicted with realistic interactions. 
+The R-matrix analysis of the results obtains for the lowest $^4$H state $E_R$=3.05$\pm$0.19 MeV and $\Gamma$=4.18$\pm$1.02 MeV while the corresponding S-matrix pole, extracted by the same authors, led to $E_R$ =1.99$\pm$0.37 MeV and $\Gamma_R$=2.85$\pm$0.3 MeV.
+Therefore, a fair comparison can only be done with other S-matrix pole predicted with realistic interactions. 
 %
@@
 %
-In this work, we observe the appearance of a stable $J^{\pi}=1^-$resonance in $^4$H using the pionless effective field theory (\eftnopi) truncated at leading order.
+In this work, we observe the existence of a stable $J^{\pi}=1^-$resonance in $^4$H using the pionless effective field theory (\eftnopi) truncated at leading order.
 The calculation is done using microscopic ab initio techniques as well as employing a folded interaction using the resonating group method (RGM).
@@
 %
-The values of the resonance energy and of the scattering parameters extracted from $S$-matrix formalism and from experiment can be hardly compared because of the very different way of extracting them, the different interpretation of the resonant state, and the difference among the experimental setups and protocol.
-However one can compare the $S$-matrix resonant poles among different theoretical calculations.
+The values of the resonance energy and of the scattering parameters extracted from S-matrix formalism and from experiment can be hardly compared because of the very different way of extracting them, the different interpretation of the resonant state, and the difference among the experimental setups and protocol.
+However one can compare the S-matrix resonant poles among different theoretical calculations.
 \eftnopi find a resonance that is sharper than other calculations performed with realistic interactions.
@@
 %
-On the qualitative point of view, the major difference between \eftnopi and the resonances found in literature is the subthreshold nature (the resonance energy is lower than the threshold energy) of the former.
-However, this is not fundamentally a problem, in part because these pole can be physical\cite{formartinanyexample}, and because a non-subtreshold resonance may still be obtained introducing orders of the EFT expansion.
+On the qualitative point of view, the major difference between \eftnopi and the resonances found in literature is the subthreshold nature of the former in the contact limit. 
+However, this is not fundamentally a problem, in part because these pole can be physical\cite{formartinanyexample}, and because a non-subthreshold resonance may still be obtained introducing higher orders of the EFT expansion.
 %
@@
 %
-The possibility of creating $P$-wave many-body poles using a contact $S$-wave theory is remarkable in itself, but it also has strong implications for \eftnopi powercounting, possibly solving the issue of the absence of stable bound states states for nuclei larger than $^4$He at LO.
-We conjecture that an existing $P$-wave resonance might be moved on the stable region by the insertion of sub-leading orders, which would be trivially impossible if no $P$-wave states are present at all.
+The possibility of creating $P$-wave many-body poles using a contact $S$-wave theory is remarkable. 
+Moreover, it also has strong implications for \eftnopi powercounting, possibly solving the issue of the absence of stable bound states states for nuclei larger than $^4$He at LO. 
+We conjecture that an existing $P$-wave resonance might be moved on the stable region by the insertion of sub-leading orders.
+This would be trivially impossible if no $P$-wave states are present at all.
 
 \section*{acknowledgement}
-We thank Bira van Kolck for the patience, discussions, and mentoring about \eftnopi and halo EFT. 
-MS was supported by the Pazy Foundation and the Israel Science Foundation grant 1086/21.
-JK acknowledges the hospitality and support of The George Washington University and the helpful
-conversations with H.~W.~Grie\ss hammer and N.~Walet.
-LC an JC supported in part by the National Science Foundation under Grant No. NSF PHY-1748958.
+We thank H.~W.~Grie\ss hammer, N.~Walet, and U.~van Kolck for helpful discussions. 
+MS was supported by the Pazy Foundation and the Israel Science Foundation grant 1086/21,
+JK by the US Department of Energy under contract DE-SC0015393, and
+LC and JC in part by the National Science Foundation under Grant No. NSF PHY-1748958.
 
